---
title: "Fitbit DailyData Metrics"
author: "Pranav Anbarasu"
date: "`r Sys.Date()`"
output:
  html_document:
    embed-resources: true
    toc: true
    toc_float:
      smooth-scroll: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = '~/RECOVER-MHDR-Analysis/')
knitr::opts_chunk$set(fig.height = 8)
knitr::opts_chunk$set(fig.width = 15)
knitr::opts_chunk$set(warning = FALSE)

```

```{r libraries and archive version, include=FALSE, warning=FALSE, message=FALSE}

library(lubridate)
library(stringr)
library(dplyr)
library(arrow)
library(tidyr)
library(synapser)
library(knit2synapse)
library(ggpubr)

synapser::synLogin(authToken = Sys.getenv("SYNAPSE_AUTH_TOKEN"))

ARCHIVE_VERSION <- "2024-05-21"

if (!(ARCHIVE_VERSION %in% list.dirs("./dashboards/fitbit-dailydata-metrics/rendered-dfs/"))) {
  dir.create(glue::glue("./dashboards/fitbit-dailydata-metrics/rendered-dfs/{ARCHIVE_VERSION}/"))
}

```

Using data from external parquet archive version: `r ARCHIVE_VERSION`

```{r helper functions, include=FALSE}

num_records_total <- function(df, measure) {
  df %>% 
    select(all_of(measure)) %>% 
    nrow()
}

num_records_complete <- function(df, measure) {
  df %>% 
    select(all_of(measure)) %>% 
    drop_na() %>% 
    nrow()
}

num_records_complete_nonzero <- function(df, measure) {
  df %>%
    select(all_of(measure)) %>%
    filter(.[[measure]]!=0) %>%
    drop_na() %>%
    nrow()
}

num_participants_with_records <- function(df, measure) {
  df$ParticipantIdentifier[!is.na(df[[measure]])] %>%
    unique() %>%
    length()
}

num_participants_with_records_nonzero <- function(df, measure) {
  df$ParticipantIdentifier[!is.na(df[[measure]]) & df[[measure]]!=0] %>%
    unique() %>%
    length()
}

days_present_nonzero_per_participant <- function(df, measure) {
  df %>% 
    select(ParticipantIdentifier, Date, measure) %>% 
    mutate(Date = as_date(Date)) %>% 
    drop_na(measure) %>% 
    filter(.[[measure]]!=0) %>%
    group_by(ParticipantIdentifier) %>% 
    distinct(Date, .keep_all = T) %>% 
    summarise(days_present_nonzero = n()) %>% 
    ungroup() %>% 
    mutate(log10_days_present_nonzero = log10(days_present_nonzero))
}

# days_present_qaqc_bounded_per_participant <- function(df, measure) {
#   df %>% 
#     select(ParticipantIdentifier, Date, measure) %>% 
#     mutate(Date = as_date(Date)) %>% 
#     drop_na(measure) %>% 
#     mutate(measure = ifelse(test = measure >= subset(bounds$lower, bounds$vars==measure) &
#                               measure <= subset(bounds$upper, bounds$vars==measure),
#                             yes = measure,
#                             no = NA)) %>%
#     group_by(ParticipantIdentifier) %>% 
#     distinct(Date, .keep_all = T) %>% 
#     summarise(days_present_nonzero = n()) %>% 
#     ungroup() %>% 
#     mutate(log10_days_present_nonzero = log10(days_present_nonzero))
# }

avg_days_present_nonzero <- function(df, col) {
  mean(df[[col]])
}

```

```{r access data, include=FALSE, message=FALSE, warning=FALSE}

synLogin(authToken = Sys.getenv("SYNAPSE_AUTH_TOKEN"))

sts_token <- 
  synapser::synGetStsStorageToken(
    entity = 'syn52506069',
    permission = 'read_only',
    output_format = 'json')

s3 <- 
  arrow::S3FileSystem$create(
    access_key = sts_token$accessKeyId,
    secret_key = sts_token$secretAccessKey,
    session_token = sts_token$sessionToken,
    region="us-east-1")

bucket_path <- paste0(sts_token$bucket, '/', 
                      sts_token$baseKey, '/', 
                      ARCHIVE_VERSION, '/')

dataset_list <- 
  s3$GetFileInfo(
    arrow::FileSelector$create(
      bucket_path, 
      recursive=F))

dataset_paths <- character()
for (dataset in dataset_list) {
  dataset_paths <- c(dataset_paths, dataset$path)
}

```

# Data Pre-Processing

```{r collect/create base datasets, include=FALSE}

bounds <- 
  data.frame(vars = c("HeartRateIntradayMinuteCount", "Steps", "SpO2_Avg", "Hrv_DailyRmssd"),
             lower = c(0, 0, 50, 3),
             upper = c(1440, 200000, 100, 210))

fitbitdailydata <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitdailydata$", dataset_paths)])) %>% 
  select(all_of(c("ParticipantIdentifier", 
                  "Date", 
                  "cohort", 
                  "HeartRateIntradayMinuteCount", 
                  "Steps", 
                  "SpO2_Avg", 
                  "Hrv_DailyRmssd"))) %>% 
  mutate(
    HeartRateIntradayMinuteCount = as.numeric(HeartRateIntradayMinuteCount),
    Steps = as.numeric(Steps),
    SpO2_Avg = as.numeric(SpO2_Avg),
    Hrv_DailyRmssd = as.numeric(Hrv_DailyRmssd)) %>% 
  rename(
    spo2_avg = SpO2_Avg,
    hrv = Hrv_DailyRmssd) %>% 
  collect() %>% 
  mutate(Date = as_date(Date))

enrolledparticipants <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_enrolledparticipants$", dataset_paths)])) %>% 
  select(ParticipantIdentifier, CustomFields_DevicesConnectedDate) %>% 
  collect()

```

**Raw data**

```{r data preprocessing}

data.frame(n_participants = 
             fitbitdailydata %>% 
             select(ParticipantIdentifier) %>% 
             n_distinct(),
           n_records = 
             fitbitdailydata %>% 
             n_distinct()) %>% 
  knitr::kable(format = "markdown", format.args = list(digits = 3, big.mark = ","))

```

**Transformation 1**: If `(Steps = 0) and (HRIMC = 0 or HRIMC = NA)`, set Steps and HRIMC to 0

<!-- The counts below are after excluding participants/records where `(Steps = 0) and (HRIMC = 0 or HRIMC = NA)` for a given record. -->

```{r steps_hrimc_filtered data, include=FALSE}
fitbitdailydata_steps_hrimc_filter <- 
  fitbitdailydata %>% 
  mutate(Steps = ifelse(test = (Steps==0 &
                                  (HeartRateIntradayMinuteCount==0 |
                                     is.na(HeartRateIntradayMinuteCount))),
                        yes = 0,
                        no = Steps),
         HeartRateIntradayMinuteCount = ifelse(test = (Steps==0 &
                                                         (HeartRateIntradayMinuteCount==0 |
                                                            is.na(HeartRateIntradayMinuteCount))),
                                               yes = 0,
                                               no = HeartRateIntradayMinuteCount))
  # filter(
  #   (!(Steps==0 & (HeartRateIntradayMinuteCount==0 | is.na(HeartRateIntradayMinuteCount)))) %>% 
  #     tidyr::replace_na(TRUE)
  #   )

data.frame(n_participants = 
             fitbitdailydata_steps_hrimc_filter %>% 
             filter(Steps>0 & HeartRateIntradayMinuteCount>0) %>% 
             select(ParticipantIdentifier) %>% 
             n_distinct(),
           n_records = 
             fitbitdailydata_steps_hrimc_filter %>% 
             filter(Steps>0 & HeartRateIntradayMinuteCount>0) %>% 
             n_distinct()) %>% 
  knitr::kable(format = "markdown", format.args = list(digits = 3, big.mark = ","))

```

**Transformation 2**: Replace records whose values are outside a pre-specified range with `NA`

```{r qa/qc range filtering, include=FALSE}

fitbitdailydata_steps_hrimc_and_qaqc_transform <- 
  fitbitdailydata_steps_hrimc_filter %>% 
  mutate(HeartRateIntradayMinuteCount = 
           ifelse(test = 
                    HeartRateIntradayMinuteCount >= subset(bounds$lower, bounds$vars=="HeartRateIntradayMinuteCount") &
                    HeartRateIntradayMinuteCount <= subset(bounds$upper, bounds$vars=="HeartRateIntradayMinuteCount"),
                  yes = HeartRateIntradayMinuteCount,
                  no = NA), 
          Steps = ifelse(test = 
                           Steps >= subset(bounds$lower, bounds$vars=="Steps") &
                           Steps <= subset(bounds$upper, bounds$vars=="Steps"),
                  yes = Steps,
                  no = NA), 
          spo2_avg = ifelse(test = 
                              spo2_avg >= subset(bounds$lower, bounds$vars=="SpO2_Avg") &
                              spo2_avg <= subset(bounds$upper, bounds$vars=="SpO2_Avg"),
                  yes = spo2_avg,
                  no = NA), 
          hrv = ifelse(test = 
                         hrv >= subset(bounds$lower, bounds$vars=="Hrv_DailyRmssd") &
                         hrv <= subset(bounds$upper, bounds$vars=="Hrv_DailyRmssd"),
                  yes = hrv,
                  no = NA))

data.frame(n_participants = 
             fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
             filter(Steps>0 & HeartRateIntradayMinuteCount>0) %>% 
             select(ParticipantIdentifier) %>% 
             n_distinct(),
           n_records = 
             fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
             filter(Steps>0 & HeartRateIntradayMinuteCount>0) %>% 
             n_distinct()) %>% 
  knitr::kable(format = "markdown", format.args = list(digits = 3, big.mark = ","))

```

# Engagement Metrics

The data resulting from applying the transformations above is used to generate the visualizations and metrics that follow.

## HeartRateIntradayMinuteCount

<!-- <details> -->

<!-- <summary>Click to Expand: Number of Participants with N Days of Non-Zero Data</summary> -->

```{r heart rate calculations, include=FALSE}

days_present_nonzero_per_participant_hr_df <- 
  days_present_nonzero_per_participant(fitbitdailydata_steps_hrimc_and_qaqc_transform, "HeartRateIntradayMinuteCount")

kd <-
  hist(
    days_present_nonzero_per_participant_hr_df$days_present_nonzero,
    # breaks = seq(0, 600, by = 50),
    labels = TRUE,
    xlab = "Number of Days",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data: Heart Rate"
  )
# axis(1, at = seq(0, 600, by = 100))

```

<!-- </details> -->

<details open>

<summary>Click to Expand: Number of Participants with N Days of Non-Zero Data Since DevicesConnectedDate</summary>


```{r heart rate calculations 2}

wear_time_devices_connected_date_df_hr <- 
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, HeartRateIntradayMinuteCount), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  drop_na() %>%
  filter(HeartRateIntradayMinuteCount!=0)

tmpdf <- 
  wear_time_devices_connected_date_df_hr %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_contributed = n()) %>% 
  select(-c(Date, HeartRateIntradayMinuteCount)) %>% 
  distinct() %>% 
  ungroup()

kd.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days of Non-Zero Data Contributed",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data Contributed Since DevicesConnectedDate: Heart Rate"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

```

</details>

<details open>

<summary>Click to Expand: Average Proportion of Non-Zero Total Wear Time Since DevicesConnectedDate</summary>

```{r heart rate calculations 3}

avg_total_wear_time_since_devices_connected_date_per_participant <- 
  wear_time_devices_connected_date_df_hr %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date>=DevicesConnectedDate) %>% 
  mutate(days_contributed = n()) %>% 
  summarise(
    avg_wear_time_mins = round(sum(HeartRateIntradayMinuteCount)/as.numeric(first(days_contributed)), 3), 
    avg_wear_time_percent = round((sum(HeartRateIntradayMinuteCount)/as.numeric(first(days_contributed)))/1440, 3))

kd2 <- density(avg_total_wear_time_since_devices_connected_date_per_participant$avg_wear_time_percent, bw = "SJ")
plot(kd2, main = "Average Proportion of Non-Zero Total Wear Time Since DevicesConnectedDate: HeartRate")
polygon(kd2, col='lightblue', border='black')

proportion_days_since_devices_connected_date_per_participant_hr <-
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, HeartRateIntradayMinuteCount), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_in_study = as.numeric(last(Date) - DevicesConnectedDate + 1)) %>% 
  select(-c(Date, HeartRateIntradayMinuteCount)) %>% 
  distinct() %>% 
  ungroup() %>% 
  right_join(y = tmpdf, by = c("ParticipantIdentifier", "DevicesConnectedDate")) %>% 
  mutate(adherence_proportion = days_contributed/days_in_study)

insights_hr <- 
  data.frame(
    "device" = "fitbit",
    "category" = "heartrate",
    "measure" = "HeartRateIntradayMinuteCount",
    "n_records" = num_records_total(fitbitdailydata_steps_hrimc_and_qaqc_transform, "HeartRateIntradayMinuteCount"),
    "n_complete" = num_records_complete(fitbitdailydata_steps_hrimc_and_qaqc_transform, "HeartRateIntradayMinuteCount"),
    "n_complete_nonzero" = num_records_complete_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "HeartRateIntradayMinuteCount"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata_steps_hrimc_and_qaqc_transform, "HeartRateIntradayMinuteCount"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "HeartRateIntradayMinuteCount"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant_hr_df, "days_present_nonzero"),
    "avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(tmpdf$days_contributed),
    "proportion_avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(proportion_days_since_devices_connected_date_per_participant_hr$adherence_proportion),
    "avg_total_wear_time_since_devices_connected_date_all_participants" = mean(avg_total_wear_time_since_devices_connected_date_per_participant$avg_wear_time_mins),
    "proportion_avg_total_wear_time_since_devices_connected_date_all_participants" = mean(avg_total_wear_time_since_devices_connected_date_per_participant$avg_wear_time_percent)
    )

```

</details>

## Steps

<!-- <details> -->

<!-- <summary>Click to Expand: Number of Participants with N Days of Non-Zero Data</summary> -->

```{r activity steps calculations, include=FALSE}

days_present_nonzero_per_participant_steps_df <- 
  days_present_nonzero_per_participant(fitbitdailydata_steps_hrimc_and_qaqc_transform, "Steps")

kd3 <- 
  hist(
    days_present_nonzero_per_participant_steps_df$days_present_nonzero, 
    breaks = seq(0, 2000, by = 100),
    labels = T,
    xlab = "Number of Days",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data: Steps"
  )
axis(1, at = seq(0, 2000, by = 100))

```

<!-- </details> -->

<details open>

<summary>Click to Expand: Number of Participants with N Days of Non-Zero Data Since DevicesConnectedDate</summary>

```{r activity steps calculations 2}

days_devices_connected_date_df_steps <- 
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, Steps), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  drop_na() %>% 
  filter(Steps!=0)

tmpdf <- 
  days_devices_connected_date_df_steps %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_contributed = n()) %>% 
  select(-c(Date, Steps)) %>% 
  distinct() %>% 
  ungroup()

kd3.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days of Non-Zero Data Contributed",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data Contributed Since DevicesConnectedDate: Steps"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

```

</details>

<details open>

<summary>Click to Expand: Proportion of Number of Days of Non-Zero Data Since DevicesConnectedDate per Participant</summary>

```{r activity steps calculations 3}

proportion_days_since_devices_connected_date_per_participant_steps <-
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, Steps), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_in_study = as.numeric(last(Date) - DevicesConnectedDate + 1)) %>% 
  select(-c(Date, Steps)) %>% 
  distinct() %>% 
  ungroup() %>% 
  right_join(y = tmpdf, by = c("ParticipantIdentifier", "DevicesConnectedDate")) %>% 
  mutate(adherence_proportion = days_contributed/days_in_study)

kd4 <- density(proportion_days_since_devices_connected_date_per_participant_steps$adherence_proportion, bw = "ucv")
plot(kd4, main = "Proportion of Number of Days of Non-Zero Data Since DevicesConnectedDate per Participant: Steps")
polygon(kd4, col='lightblue', border='black')

insights_steps <- 
  data.frame(
    "device" = "fitbit",
    "category" = "steps",
    "measure" = "Steps",
    "n_records" = num_records_total(fitbitdailydata_steps_hrimc_and_qaqc_transform, "Steps"),
    "n_complete" = num_records_complete(fitbitdailydata_steps_hrimc_and_qaqc_transform, "Steps"),
    "n_complete_nonzero" = num_records_complete_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "Steps"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata_steps_hrimc_and_qaqc_transform, "Steps"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "Steps"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant_steps_df, "days_present_nonzero"),
    "avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(tmpdf$days_contributed),
    "proportion_avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(proportion_days_since_devices_connected_date_per_participant_steps$adherence_proportion)
  )

```

</details>

## SpO2

<!-- <details> -->

<!-- <summary>Click to Expand: Number of Participants with N Days of Non-Zero Data</summary> -->

```{r spo2 calculations, include=FALSE}

days_present_nonzero_per_participant_spo2_df <- 
  days_present_nonzero_per_participant(fitbitdailydata_steps_hrimc_and_qaqc_transform, "spo2_avg")

kd5 <- 
  hist(
    days_present_nonzero_per_participant_spo2_df$days_present_nonzero, 
    # breaks = seq(0, 600, by = 50),
    labels = T,
    xlab = "Number of Days",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data: SpO2"
  )
# axis(1, at = seq(0, 600, by = 100))

```

<!-- </details> -->

<details open>

<summary>Click to Expand: Number of Participants with N Days of Non-Zero Data Since DevicesConnectedDate</summary>

```{r spo2 calculations 2}

days_devices_connected_date_df_spo2 <- 
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, spo2_avg), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  drop_na() %>% 
  filter(spo2_avg!=0)

tmpdf <- 
  days_devices_connected_date_df_spo2 %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_contributed = n()) %>% 
  select(-c(Date, spo2_avg)) %>% 
  distinct() %>% 
  ungroup()

kd5.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days of Non-Zero Data Contributed",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data Contributed Since DevicesConnectedDate: SpO2"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

```

</details>

<details open>

<summary>Click to Expand: Proportion of Number of Days of Non-Zero Data Since DevicesConnectedDate per Participant</summary>

```{r spo2 calculations 3}

proportion_days_since_devices_connected_date_per_participant_spo2 <-
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, spo2_avg), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_in_study = as.numeric(last(Date) - DevicesConnectedDate + 1)) %>% 
  select(-c(Date, spo2_avg)) %>% 
  distinct() %>% 
  ungroup() %>% 
  right_join(y = tmpdf, by = c("ParticipantIdentifier", "DevicesConnectedDate")) %>% 
  mutate(adherence_proportion = days_contributed/days_in_study)
  
kd6 <- density(proportion_days_since_devices_connected_date_per_participant_spo2$adherence_proportion, bw = "ucv")
plot(kd6, main = "Proportion of Number of Days of Non-Zero Data Since DevicesConnectedDate per Participant: SpO2")
polygon(kd6, col='lightblue', border='black')

insights_spo2 <- 
  data.frame(
    "device" = "fitbit",
    "category" = "spo2",
    "measure" = "SpO2_Avg",
    "n_records" = num_records_total(fitbitdailydata_steps_hrimc_and_qaqc_transform, "spo2_avg"),
    "n_complete" = num_records_complete(fitbitdailydata_steps_hrimc_and_qaqc_transform, "spo2_avg"),
    "n_complete_nonzero" = num_records_complete_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "spo2_avg"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata_steps_hrimc_and_qaqc_transform, "spo2_avg"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "spo2_avg"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant_spo2_df, "days_present_nonzero"),
    "avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(tmpdf$days_contributed),
    "proportion_avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(proportion_days_since_devices_connected_date_per_participant_spo2$adherence_proportion)
  )

```

</details>

## HRV

<!-- <details> -->

<!-- <summary>Click to Expand: Number of Participants with N Days of Non-Zero Data</summary> -->

```{r hrv calculations, include=FALSE}

days_present_nonzero_per_participant_hrv_df <- 
  days_present_nonzero_per_participant(fitbitdailydata_steps_hrimc_and_qaqc_transform, "hrv")

kd7 <- 
  hist(
    days_present_nonzero_per_participant_hrv_df$days_present_nonzero, 
    breaks = seq(0, 1000, by = 50),
    labels = T,
    xlab = "Number of Days",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data: HRV"
  )
axis(1, at = seq(0, 1000, by = 100))

```

<!-- </details> -->

<details open>

<summary>Click to Expand: Number of Participants with N Days of Non-Zero Data Since DevicesConnectedDate</summary>

```{r hrv calculations 2}

days_devices_connected_date_df_hrv <- 
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, hrv), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  drop_na() %>% 
  filter(hrv!=0)

tmpdf <- 
  days_devices_connected_date_df_hrv %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_contributed = n()) %>% 
  select(-c(Date, hrv)) %>% 
  distinct() %>% 
  ungroup()

kd7.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days of Non-Zero Data Contributed",
    ylab = "Number of Participants",
    main = "Number of Participants with N Days of Non-Zero Data Contributed Since DevicesConnectedDate: HRV"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

```

</details>

<details open>

<summary>Click to Expand: Proportion of Number of Days of Non-Zero Data Since DevicesConnectedDate per Participant</summary>

```{r hrv calculations 3}

proportion_days_since_devices_connected_date_per_participant_hrv <-
  merge(x = 
          fitbitdailydata_steps_hrimc_and_qaqc_transform %>% 
          select(ParticipantIdentifier, Date, hrv), 
        y = 
          enrolledparticipants %>% 
          select(ParticipantIdentifier, CustomFields_DevicesConnectedDate)) %>% 
  rename(DevicesConnectedDate = CustomFields_DevicesConnectedDate) %>% 
  mutate(Date = as_date(Date),
         DevicesConnectedDate = as_date(DevicesConnectedDate)) %>% 
  group_by(ParticipantIdentifier) %>% 
  arrange(Date, .by_group = TRUE) %>% 
  filter(Date >= DevicesConnectedDate) %>% 
  mutate(days_in_study = as.numeric(last(Date) - DevicesConnectedDate + 1)) %>% 
  select(-c(Date, hrv)) %>% 
  distinct() %>% 
  ungroup() %>% 
  right_join(y = tmpdf, by = c("ParticipantIdentifier", "DevicesConnectedDate")) %>% 
  mutate(adherence_proportion = days_contributed/days_in_study)

kd8 <- density(proportion_days_since_devices_connected_date_per_participant_hrv$adherence_proportion, bw = "ucv")
plot(kd8, main = "Proportion of Number of Days of Non-Zero Data Since DevicesConnectedDate per Participant: HRV")
polygon(kd8, col='lightblue', border='black')

insights_hrv <- 
  data.frame(
    "device" = "fitbit",
    "category" = "hrv",
    "measure" = "Hrv_DailyRmssd",
    "n_records" = num_records_total(fitbitdailydata_steps_hrimc_and_qaqc_transform, "hrv"),
    "n_complete" = num_records_complete(fitbitdailydata_steps_hrimc_and_qaqc_transform, "hrv"),
    "n_complete_nonzero" = num_records_complete_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "hrv"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata_steps_hrimc_and_qaqc_transform, "hrv"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata_steps_hrimc_and_qaqc_transform, "hrv"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant_hrv_df, "days_present_nonzero"),
    "avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(tmpdf$days_contributed),
    "proportion_avg_n_days_contributed_since_devices_connected_date_all_participants" = mean(proportion_days_since_devices_connected_date_per_participant_hrv$adherence_proportion)
  )

```

</details>

## Summary

```{r bind all calculations dfs}

insights <- bind_rows(insights_hr, insights_steps, insights_spo2, insights_hrv)

fitbit_dailydata_metrics <- 
  data.frame(type = insights$category, 
             n_participants = insights$n_participants_with_complete_nonzero_records,
             n_records = insights$n_complete_nonzero, 
             avg_days = round(insights$avg_n_days_of_complete_nonzero_data, 1), 
             avg_days_since_connected = round(insights$avg_n_days_contributed_since_devices_connected_date_all_participants, 1),
             prop_avg_days_since_connected = round(insights$proportion_avg_n_days_contributed_since_devices_connected_date_all_participants, 3))

write.csv(insights, 
          paste0("dashboards/fitbit-dailydata-metrics/rendered-dfs/", ARCHIVE_VERSION, "/insights.csv"), 
          row.names = F)

write.csv(fitbit_dailydata_metrics, 
          paste0("dashboards/fitbit-dailydata-metrics/rendered-dfs/", ARCHIVE_VERSION, "/fitbit_dailydata_metrics.csv"),
          row.names = F)

```

### At a Glance

<details open>

<summary>Click to Expand</summary>

```{r At a glance, echo=FALSE}

fitbit_dailydata_metrics %>% 
  knitr::kable(format = "markdown", 
               format.args = list(big.mark = ","))

```

**Note:**
- `n_participants` = Number of unique participants with complete non-zero records
- `n_records` = Number of complete non-zero records
- `avg_days` = Average number of days of complete non-zero data
- `avg_days_since_connected` = Average number of days of complete non-zero data since `DevicesConnectedDate` across all participants (number of days where data was contributed)
- `prop_avg_days_since_connected` = Proportion of average number of days of complete non-zero data since `DevicesConnectedDate` across all participants (number of days where data was contributed divided by number of days in study)

</details>

### Number of Records

<details>

<summary>Click to Expand</summary>

```{r insights table num records, echo=FALSE}

insights %>% 
  select(all_of(c("category", 
                  "measure", 
                  # "n_records", 
                  "n_complete", 
                  "n_complete_nonzero"))) %>% 
  knitr::kable(format = "markdown",
               format.args = list(big.mark = ",",
                                  scientific = F))

```

**Note:**
<!-- - `n_records` = Number of records -->
- `n_complete` = Number of complete records
- `n_complete_nonzero` = Number of complete non-zero records

</details>

### Number of Participants

<details>

<summary>Click to Expand</summary>

```{r insights table num participants, echo=FALSE}

insights %>% 
  select(all_of(c("category", 
                  "measure", 
                  "n_participants_with_complete_records", 
                  "n_participants_with_complete_nonzero_records"))) %>% 
  rename(n_participants = n_participants_with_complete_records,
         n_participants_complete_nonzero = n_participants_with_complete_nonzero_records) %>% 
  knitr::kable(format = "markdown")

```

**Note:**
- `n_participants` = Number of unique participants with complete records
- `n_participants_complete_nonzero` = Number of unique participants with complete non-zero records

</details>

### Number of Days of Data

<details>

<summary>Click to Expand</summary>

```{r insights table num days of data, echo=FALSE}

insights %>% 
  select(all_of(c("category", 
                  "measure", 
                  "avg_n_days_of_complete_nonzero_data", 
                  "avg_n_days_contributed_since_devices_connected_date_all_participants",
                  "proportion_avg_n_days_contributed_since_devices_connected_date_all_participants"))) %>% 
  rename(avg_days = avg_n_days_of_complete_nonzero_data,
         avg_days_since_connected = avg_n_days_contributed_since_devices_connected_date_all_participants,
         prop_avg_days_since_connected = proportion_avg_n_days_contributed_since_devices_connected_date_all_participants) %>% 
  knitr::kable(format = "markdown", 
               format.args = list(digits = 3))

```

**Note:** 
- `avg_days` = Average number of days of complete non-zero data
- `avg_days_since_connected` = Average number of days of complete non-zero data since `DevicesConnectedDate` across all participants (number of days where data was contributed)
- `prop_avg_days_since_connected` = Proportion of average number of days of complete non-zero data since `DevicesConnectedDate` across all participants (number of days where data was contributed divided by number of days in study)


</details>

### Average Device Wear Time

<details>

<summary>Click to Expand</summary>

```{r insights table avg wear time, echo=FALSE}

insights %>% 
  select(all_of(c("category", 
                  "measure", 
                  "avg_total_wear_time_since_devices_connected_date_all_participants", 
                  "proportion_avg_total_wear_time_since_devices_connected_date_all_participants"))) %>% 
  filter(measure == "HeartRateIntradayMinuteCount") %>% 
  rename(avg_total_wear_time = avg_total_wear_time_since_devices_connected_date_all_participants,
         prop_avg_total_wear_time = proportion_avg_total_wear_time_since_devices_connected_date_all_participants) %>% 
  knitr::kable(format = "markdown",
               format.args = list(digits = 3))

```

**Note:**
- `avg_total_wear_time` = Average total wear time (minutes) since `DevicesConnectedDate` across all participants
- `prop_avg_total_wear_time` = Proportion of average total wear time since `DevicesConnectedDate` across all participants (avg wear time divided 1440 minutes)

</details>

## Code used 

```{r provenance, echo=FALSE, results='asis'}

this_file_path <- "dashboards/fitbit-dailydata-metrics/fitbit-dailydata-metrics.Rmd"

latest_file_commit <- 
  gh::gh("/repos/:owner/:repo/commits", 
         owner = "pranavanba", 
         repo = "RECOVER-MHDR-Analysis", 
         path = this_file_path, 
         .token = readLines("~/git_token.txt"))[[1]]$commit$url %>% 
  {gsub("https://api.github.com/repos/", "https://github.com/", .)} %>% {gsub("/git/commits/", "/blob/", .)} %>% glue::glue("/{this_file_path}")

cat("[Link to GitHub repo](", latest_file_commit, ")")

```
