---
title: "Fitbit DailyData Metrics"
author: "Pranav Anbarasu"
date: "`r Sys.Date()`"
output:
  html_document:
    embed-resources: true
    toc: true
    toc_float:
      smooth-scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = '~/RECOVER-MHDR-Analysis/')
knitr::opts_chunk$set(fig.height = 8)
knitr::opts_chunk$set(fig.width = 15)
knitr::opts_chunk$set(warning = FALSE)
```

```{r libraries and archive version, include=FALSE, warning=FALSE, message=FALSE}
library(lubridate)
library(stringr)
library(dplyr)
library(arrow)
library(tidyr)
library(synapser)
library(knit2synapse)
library(ggpubr)

synapser::synLogin(authToken = Sys.getenv("SYNAPSE_AUTH_TOKEN"))

ARCHIVE_VERSION <- "2024-02-01"

if (!(ARCHIVE_VERSION %in% list.dirs("./dashboards/fitbit-dailydata-metrics/rendered-dfs/"))) {
  dir.create(glue::glue("./dashboards/fitbit-dailydata-metrics/rendered-dfs/{ARCHIVE_VERSION}/"))
}
```

```{r access data, include=FALSE, message=FALSE, warning=FALSE}
synLogin(authToken = Sys.getenv("SYNAPSE_AUTH_TOKEN"))

sts_token <- 
  synapser::synGetStsStorageToken(
    entity = 'syn52506069',
    permission = 'read_only',
    output_format = 'json')

s3 <- 
  arrow::S3FileSystem$create(
    access_key = sts_token$accessKeyId,
    secret_key = sts_token$secretAccessKey,
    session_token = sts_token$sessionToken,
    region="us-east-1")

bucket_path <- paste0(sts_token$bucket, '/', 
                      sts_token$baseKey, '/', 
                      ARCHIVE_VERSION, '/')

dataset_list <- 
  s3$GetFileInfo(
    arrow::FileSelector$create(
      bucket_path, 
      recursive=F))

dataset_paths <- character()
for (dataset in dataset_list) {
  dataset_paths <- c(dataset_paths, dataset$path)
}
```

```{r open datasets, include=FALSE}
fitbitdailydata <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitdailydata$", dataset_paths)])) %>% 
  select(all_of(c("ParticipantIdentifier", 
                  "Date", 
                  "cohort", 
                  "HeartRateIntradayMinuteCount", 
                  "Steps", 
                  "SpO2_Avg", 
                  "Hrv_DailyRmssd"))) %>% 
  mutate(
    HeartRateIntradayMinuteCount = as.numeric(HeartRateIntradayMinuteCount),
    Steps = as.numeric(Steps),
    SpO2_Avg = as.numeric(SpO2_Avg),
    Hrv_DailyRmssd = as.numeric(Hrv_DailyRmssd)) %>% 
  collect() %>% 
  # filter((!(Steps==0 & (HeartRateIntradayMinuteCount==0 | is.na(HeartRateIntradayMinuteCount)))) %>%
  #          tidyr::replace_na(TRUE)) %>% 
  rename(
    spo2_avg = SpO2_Avg,
    hrv = Hrv_DailyRmssd)

enrolledparticipants <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_enrolledparticipants$", dataset_paths)])) %>% 
  collect()
```

```{r helper functions, include=FALSE}
num_records_total <- function(df, measure) {
  df %>% 
    select(all_of(measure)) %>% 
    nrow()
}

num_records_complete <- function(df, measure) {
  df %>% 
    select(all_of(measure)) %>% 
    drop_na() %>% 
    nrow()
}

num_records_complete_nonzero <- function(df, measure) {
  df %>%
    select(all_of(measure)) %>%
    filter(.[[measure]]!=0) %>%
    drop_na() %>%
    nrow()
}

num_participants_with_records <- function(df, measure) {
  df$ParticipantIdentifier[
    !is.na(df[[measure]])
  ] %>%
    unique() %>%
    length()
}

num_participants_with_records_nonzero <- function(df, measure) {
  df$ParticipantIdentifier[
    !is.na(df[[measure]]) &
      df[[measure]]!=0
  ] %>%
    unique() %>%
    length()
}

days_present_nonzero_per_participant <- function(df, measure) {
  df %>% 
    select(ParticipantIdentifier, Date, measure) %>% 
    mutate(Date = as_date(Date)) %>% 
    drop_na() %>% 
    filter(.[[measure]]!=0) %>% 
    group_by(ParticipantIdentifier) %>% 
    distinct(Date, .keep_all = T) %>% 
    summarise(days_present_nonzero = n()) %>% 
    ungroup() %>% 
    mutate(log10_days_present_nonzero = log10(days_present_nonzero))
}

avg_days_present_nonzero <- function(df, col) {
  mean(df[[col]])
}
```

## Heart Rate

```{r heart rate calculations}
days_present_nonzero_per_participant_hr_df <- 
  days_present_nonzero_per_participant(fitbitdailydata, "HeartRateIntradayMinuteCount")

# kd <- 
#   ggoutlier::ggoutlier_hist(
#     days_present_nonzero_per_participant_hr_df,
#     var_name = "days_present_nonzero",
#     cut_off_ceiling = 365,
#     binwidth = 50,
#   ) + 
#   # ggplot(days_present_nonzero_per_participant_hr_df, aes(x = days_present_nonzero)) +
#   geom_histogram(binwidth = 50, boundary = 0)  # Modify parameters as needed
# 
# kd

kd <-
  hist(
    days_present_nonzero_per_participant_hr_df$days_present_nonzero,
    # breaks = seq(0, 1100, by = 50),
    labels = TRUE,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data: Heart Rate"
  )
axis(1, at = seq(0, 1100, by = 100))

# days_present_nonzero_per_participant_hr_df %>%
#   ggpubr::gghistogram(x = "days_present_nonzero",
#                       y = "count",
#                       fill = "lightgray",
#                       xlab = "Number of Days of Non-Zero Data (log10 scale)",
#                       title = "Number of Days of Data per Participant") +
#   scale_x_log10()
# 
# days_present_nonzero_per_participant_hr_df%>%
#   ggplot(aes(x=days_present_nonzero)) +
#   geom_histogram() +
#   geom_text(aes(label = after_stat(count)), stat = "count", vjust=-1, size=3) +
#   scale_x_log10() +
#   labs(x= "Number of Days of Non-Zero Data (log10 scale)",
#        title = "Number of Days of Data per Participant")

# kd <- density(days_present_nonzero_per_participant_hr_df$days_present_nonzero, bw = "SJ")
# plot(kd,
#      main = "Number of Days of Data per Participant",
#      sub = "HeartRate: HeartRateIntradayMinuteCount != 0")
# polygon(kd, col='lightblue', border='black')

wear_time_enrollment_df_hr <- 
  merge(x = fitbitdailydata %>% select(ParticipantIdentifier, Date, HeartRateIntradayMinuteCount), 
             y = enrolledparticipants %>% select(ParticipantIdentifier, EnrollmentDate)) %>% 
  mutate(Date = as_date(Date),
         EnrollmentDate = as_date(EnrollmentDate)) %>% 
  drop_na() %>% 
  filter(HeartRateIntradayMinuteCount!=0)

tmpdf <- 
  wear_time_enrollment_df_hr %>% 
  group_by(ParticipantIdentifier) %>% 
  filter(Date >= EnrollmentDate) %>% 
  mutate(most_recent_date = max(Date)) %>% 
  mutate(days_contributed = as.numeric(most_recent_date - first(Date) + 1)) %>% 
  mutate(days_in_study = as.numeric(most_recent_date - EnrollmentDate + 1)) %>% 
  select(-c(Date, HeartRateIntradayMinuteCount)) %>% 
  distinct() %>% 
  ungroup()

kd.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data Since Enrollment: Heart Rate"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

avg_total_wear_time_since_enrollment_per_participant <- 
  wear_time_enrollment_df_hr %>% 
  group_by(ParticipantIdentifier) %>% 
  filter(Date>=EnrollmentDate) %>% 
  mutate(last_date = max(Date)) %>% 
  mutate(days = last_date-EnrollmentDate+1) %>% 
  mutate(n = n()) %>% 
  summarise(
    avg_wear_time_mins = round(sum(HeartRateIntradayMinuteCount)/as.numeric(first(days)), 3), 
    avg_wear_time_percent = round((sum(HeartRateIntradayMinuteCount)/as.numeric(first(days)))/1439, 3))

kd2 <- density(avg_total_wear_time_since_enrollment_per_participant$avg_wear_time_percent, bw = "SJ")
plot(kd2, main = "Average Proportion of Non-Zero Total Wear Time Since Enrollment: HeartRate")
polygon(kd2, col='lightblue', border='black')

days_enrollment_df_hr <- 
  merge(x = fitbitdailydata %>% select(ParticipantIdentifier, Date, HeartRateIntradayMinuteCount), 
        y = enrolledparticipants %>% select(ParticipantIdentifier, EnrollmentDate)) %>% 
  mutate(Date = as_date(Date),
         EnrollmentDate = as_date(EnrollmentDate)) %>% 
  drop_na() %>% 
  filter(HeartRateIntradayMinuteCount!=0)

proportion_days_since_enrollment_per_participant_hr <-
  days_enrollment_df_hr %>%
  group_by(ParticipantIdentifier) %>%
  filter(Date>=EnrollmentDate) %>%
  summarise(n_days = n(),
            dt = as.numeric(max(Date)-min(EnrollmentDate)+1)) %>% 
  mutate(adherence_proportion = n_days/dt)

insights_hr <- 
  data.frame(
    "device" = "fitbit",
    "category" = "heartrate",
    "measure" = "HeartRateIntradayMinuteCount",
    "n_records" = num_records_total(fitbitdailydata, "HeartRateIntradayMinuteCount"),
    "n_complete_records" = num_records_complete(fitbitdailydata, "HeartRateIntradayMinuteCount"),
    "n_complete_nonzero_records" = num_records_complete_nonzero(fitbitdailydata, "HeartRateIntradayMinuteCount"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata, "HeartRateIntradayMinuteCount"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata, "HeartRateIntradayMinuteCount"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant_hr_df, "days_present_nonzero"),
    "avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_hr$n_days),
    "proportion_avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_hr$adherence_proportion),
    "avg_total_wear_time_since_enrollment_all_participants" = mean(avg_total_wear_time_since_enrollment_per_participant$avg_wear_time_mins),
    "proportion_avg_total_wear_time_since_enrollment_all_participants" = mean(avg_total_wear_time_since_enrollment_per_participant$avg_wear_time_percent)
    )
```

## Steps (Activity)

```{r activity steps calculations}
days_present_nonzero_per_participant_steps_df <- 
  days_present_nonzero_per_participant(fitbitdailydata, "Steps")

kd3 <- 
  hist(
    days_present_nonzero_per_participant_steps_df$days_present_nonzero, 
    breaks = seq(0, 2000, by = 50),
    labels = T,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data: Steps (Activity)"
  )
axis(1, at = seq(0, 2000, by = 100))

# kd3 <- density(days_present_nonzero_per_participant_steps_df$days_present_nonzero, bw = "SJ")
# plot(kd3, main = "Number of Days of Data per Participant", sub = "Activity: Steps")
# polygon(kd3, col='lightblue', border='black')

days_enrollment_df_steps <- 
  merge(x = fitbitdailydata %>% select(ParticipantIdentifier, Date, Steps), 
        y = enrolledparticipants %>% select(ParticipantIdentifier, EnrollmentDate)) %>% 
  mutate(Date = as_date(Date),
         EnrollmentDate = as_date(EnrollmentDate)) %>% 
  drop_na() %>% 
  filter(Steps!=0)

tmpdf <- 
  days_enrollment_df_steps %>% 
  group_by(ParticipantIdentifier) %>% 
  filter(Date >= EnrollmentDate) %>% 
  mutate(most_recent_date = max(Date)) %>% 
  mutate(days_contributed = as.numeric(most_recent_date - first(Date) + 1)) %>% 
  mutate(days_in_study = as.numeric(most_recent_date - EnrollmentDate + 1)) %>% 
  select(-c(Date, Steps)) %>% 
  distinct() %>% 
  ungroup()

kd3.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data Since Enrollment: Steps"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

proportion_days_since_enrollment_per_participant_steps <-
  days_enrollment_df_steps %>%
  group_by(ParticipantIdentifier) %>%
  filter(Date>=EnrollmentDate) %>%
  summarise(n_days = n(),
            dt = as.numeric(max(Date)-min(EnrollmentDate)+1)) %>% 
  mutate(adherence_proportion = n_days/dt)

kd4 <- density(proportion_days_since_enrollment_per_participant_steps$adherence_proportion, bw = "ucv")
plot(kd4, main = "Proportion of Number of Days of Non-Zero Data Since Enrollment per Participant: Steps (Activity)")
polygon(kd4, col='lightblue', border='black')

insights_steps <- 
  data.frame(
    "device" = "fitbit",
    "category" = "activity",
    "measure" = "steps",
    "n_records" = num_records_total(fitbitdailydata, "Steps"),
    "n_complete_records" = num_records_complete(fitbitdailydata, "Steps"),
    "n_complete_nonzero_records" = num_records_complete_nonzero(fitbitdailydata, "Steps"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata, "Steps"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata, "Steps"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant(fitbitdailydata, "Steps"), "days_present_nonzero"),
    "avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_steps$n_days),
    "proportion_avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_steps$adherence_proportion)
  )
```

## SpO2

```{r spo2 calculations}
days_present_nonzero_per_participant_spo2_df <- 
  days_present_nonzero_per_participant(fitbitdailydata, "spo2_avg")

kd5 <- 
  hist(
    days_present_nonzero_per_participant_spo2_df$days_present_nonzero, 
    # breaks = seq(0, 600, by = 50),
    labels = T,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data: SpO2"
  )
axis(1, at = seq(0, 600, by = 100))

# kd5 <- density(days_present_nonzero_per_participant_spo2_df$days_present_nonzero, bw = "SJ")
# plot(kd5, main = "Number of Days of Data per Participant", sub = "spo2")
# polygon(kd5, col='lightblue', border='black')

days_enrollment_df_spo2 <- 
  merge(x = fitbitdailydata %>% select(ParticipantIdentifier, Date, spo2_avg), 
        y = enrolledparticipants %>% select(ParticipantIdentifier, EnrollmentDate)) %>% 
  mutate(Date = as_date(Date),
         EnrollmentDate = as_date(EnrollmentDate)) %>% 
  drop_na() %>% 
  filter(spo2_avg!=0)

tmpdf <- 
  days_enrollment_df_spo2 %>% 
  group_by(ParticipantIdentifier) %>% 
  filter(Date >= EnrollmentDate) %>% 
  mutate(most_recent_date = max(Date)) %>% 
  mutate(days_contributed = as.numeric(most_recent_date - first(Date) + 1)) %>% 
  mutate(days_in_study = as.numeric(most_recent_date - EnrollmentDate + 1)) %>% 
  select(-c(Date, spo2_avg)) %>% 
  distinct() %>% 
  ungroup()

kd5.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data Since Enrollment: SpO2"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

proportion_days_since_enrollment_per_participant_spo2 <-
  days_enrollment_df_spo2 %>%
  group_by(ParticipantIdentifier) %>%
  filter(Date>=EnrollmentDate) %>%
  summarise(n_days = n(),
            dt = as.numeric(max(Date)-min(EnrollmentDate)+1)) %>% 
  mutate(adherence_proportion = n_days/dt)

kd6 <- density(proportion_days_since_enrollment_per_participant_spo2$adherence_proportion, bw = "ucv")
plot(kd6, main = "Proportion of Number of Days of Non-Zero Data Since Enrollment per Participant: SpO2")
polygon(kd6, col='lightblue', border='black')

insights_spo2 <- 
  data.frame(
    "device" = "fitbit",
    "category" = "spo2",
    "measure" = "spo2",
    "n_records" = num_records_total(fitbitdailydata, "spo2_avg"),
    "n_complete_records" = num_records_complete(fitbitdailydata, "spo2_avg"),
    "n_complete_nonzero_records" = num_records_complete_nonzero(fitbitdailydata, "spo2_avg"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata, "spo2_avg"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata, "spo2_avg"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant(fitbitdailydata, "spo2_avg"), "days_present_nonzero"),
    "avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_spo2$n_days),
    "proportion_avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_spo2$adherence_proportion)
  )

```

## HRV

```{r hrv calculations}
days_present_nonzero_per_participant_hrv_df <- days_present_nonzero_per_participant(fitbitdailydata, "hrv")

kd7 <- 
  hist(
    days_present_nonzero_per_participant_hrv_df$days_present_nonzero, 
    # breaks = seq(0, 800, by = 50),
    labels = T,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data: HRV"
  )
axis(1, at = seq(0, 800, by = 100))

# kd7 <- density(days_present_nonzero_per_participant_hrv_df$days_present_nonzero, bw = "SJ")
# plot(kd7, main = "Number of Days of Data per Participant", sub = "hrv")
# polygon(kd7, col='lightblue', border='black')

days_enrollment_df_hrv <- 
  merge(x = fitbitdailydata %>% select(ParticipantIdentifier, Date, hrv), 
        y = enrolledparticipants %>% select(ParticipantIdentifier, EnrollmentDate)) %>% 
  mutate(Date = as_date(Date),
         EnrollmentDate = as_date(EnrollmentDate)) %>% 
  drop_na() %>% 
  filter(hrv!=0)

tmpdf <- 
  days_enrollment_df_hrv %>% 
  group_by(ParticipantIdentifier) %>% 
  filter(Date >= EnrollmentDate) %>% 
  mutate(most_recent_date = max(Date)) %>% 
  mutate(days_contributed = as.numeric(most_recent_date - first(Date) + 1)) %>% 
  mutate(days_in_study = as.numeric(most_recent_date - EnrollmentDate + 1)) %>% 
  select(-c(Date, hrv)) %>% 
  distinct() %>% 
  ungroup()

kd5.2 <- 
  hist(
    tmpdf$days_contributed,
    breaks = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 25),
    labels = TRUE,
    xlab = "Number of Days",
    ylab = "Count",
    main = "Number of Participants with N Days of Non-Zero Data Since Enrollment: HRV"
  )
axis(1, at = seq(0, (round((max(tmpdf$days_contributed)/1000), 1) * 1000 + 50), by = 50))

proportion_days_since_enrollment_per_participant_hrv <-
  days_enrollment_df_hrv %>%
  group_by(ParticipantIdentifier) %>%
  filter(Date>=EnrollmentDate) %>%
  summarise(n_days = n(),
            dt = as.numeric(max(Date)-min(EnrollmentDate)+1)) %>% 
  mutate(adherence_proportion = n_days/dt)

kd8 <- density(proportion_days_since_enrollment_per_participant_hrv$adherence_proportion, bw = "ucv")
plot(kd8, main = "Proportion of Number of Days of Non-Zero Data Since Enrollment per Participant: HRV")
polygon(kd8, col='lightblue', border='black')

insights_hrv <- 
  data.frame(
    "device" = "fitbit",
    "category" = "hrv",
    "measure" = "hrv",
    "n_records" = num_records_total(fitbitdailydata, "hrv"),
    "n_complete_records" = num_records_complete(fitbitdailydata, "hrv"),
    "n_complete_nonzero_records" = num_records_complete_nonzero(fitbitdailydata, "hrv"),
    "n_participants_with_complete_records" = num_participants_with_records(fitbitdailydata, "hrv"),
    "n_participants_with_complete_nonzero_records" = num_participants_with_records_nonzero(fitbitdailydata, "hrv"),
    "avg_n_days_of_complete_nonzero_data" = avg_days_present_nonzero(days_present_nonzero_per_participant(fitbitdailydata, "hrv"), "days_present_nonzero"),
    "avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_hrv$n_days),
    "proportion_avg_n_days_since_enrollment_all_participants" = mean(proportion_days_since_enrollment_per_participant_hrv$adherence_proportion)
  )
```

## Insights and Metrics Tables

```{r bind all four calculations dfs}
insights <- bind_rows(insights_hr, insights_steps, insights_spo2, insights_hrv)

fitbit_dailydata_metrics <- 
  data.frame(type = insights$category, 
             n_participants = insights$n_participants_with_complete_nonzero_records,
             n_records = insights$n_complete_nonzero_records, 
             avg_n_days = round(insights$avg_n_days_of_complete_nonzero_data, 1), 
             avg_n_days_since_enroll = round(insights$avg_n_days_since_enrollment_all_participants, 1),
             prop_avg_n_days_since_enroll = round(insights$proportion_avg_n_days_since_enrollment_all_participants, 3))

write.csv(insights, 
          paste0("dashboards/fitbit-dailydata-metrics/rendered-dfs/", ARCHIVE_VERSION, "/insights.csv"), 
          row.names = F)

write.csv(fitbit_dailydata_metrics, 
          paste0("dashboards/fitbit-dailydata-metrics/rendered-dfs/", ARCHIVE_VERSION, "/fitbit_dailydata_metrics.csv"),
          row.names = F)
```

### At a Glance

```{r At a glance, echo=FALSE}
fitbit_dailydata_metrics %>% 
  knitr::kable(format = "markdown", 
               format.args = list(big.mark = ","))
```

**Note:**
- `n_participants` = Number of unique participants with complete non-zero records
- `n_records` = Number of complete non-zero records
- `avg_n_days` = Average number of days of complete non-zero data
- `avg_n_days_since_enroll` = Average number of days of complete non-zero data since enrollment across all participants
- `prop_avg_n_days_since_enroll` = Proportion of average number of days of complete non-zero data since enrollment across all participants


### Number of Records

```{r insights table num records, echo=FALSE}
insights %>% 
  select(all_of(c("device", 
                  "category", 
                  "measure", 
                  "n_records", 
                  "n_complete_records", 
                  "n_complete_nonzero_records"))) %>% 
  knitr::kable(format = "markdown",
               format.args = list(big.mark = ",",
                                  scientific = F))
```

### Number of Participants

```{r insights table num participants, echo=FALSE}
insights %>% 
  select(all_of(c("device", 
                  "category", 
                  "measure", 
                  "n_participants_with_complete_records", 
                  "n_participants_with_complete_nonzero_records"))) %>% 
  rename(n_participants = n_participants_with_complete_records,
         n_participants_nonzero_records = n_participants_with_complete_nonzero_records) %>% 
  knitr::kable(format = "markdown")
```

**Note:**
- `n_participants` = Number of unique participants with complete records
- `n_participants_nonzero_records` = Number of unique participants with complete non-zero records


### Number of Days of Data

```{r insights table num days of data, echo=FALSE}
insights %>% 
  select(all_of(c("device", 
                  "category", 
                  "measure", 
                  "avg_n_days_of_complete_nonzero_data", 
                  "avg_n_days_since_enrollment_all_participants",
                  "proportion_avg_n_days_since_enrollment_all_participants"))) %>% 
  rename(avg_n_days_all_data = avg_n_days_of_complete_nonzero_data,
         avg_n_days_since_enroll = avg_n_days_since_enrollment_all_participants,
         prop_avg_n_days_since_enroll = proportion_avg_n_days_since_enrollment_all_participants) %>% 
  knitr::kable(format = "markdown", 
               format.args = list(digits = 3))
```

**Note:** 
- `avg_n_days_all_data` = Average number of days of complete non-zero data
- `avg_n_days_since_enroll` = Average number of days of complete non-zero data since enrollment across all participants
- `avg_n_days_since_enroll` = Proportion of average number of days of complete non-zero data since enrollment across all participants

### Average Device Wear Time

```{r insights table avg wear time, echo=FALSE}
insights %>% 
  select(all_of(c("device", 
                  "category", 
                  "measure", 
                  "avg_total_wear_time_since_enrollment_all_participants", 
                  "proportion_avg_total_wear_time_since_enrollment_all_participants"))) %>% 
  filter(measure == "HeartRateIntradayMinuteCount") %>% 
  rename(avg_total_wear_time = avg_total_wear_time_since_enrollment_all_participants,
         prop_avg_total_wear_time = proportion_avg_total_wear_time_since_enrollment_all_participants) %>% 
  knitr::kable(format = "markdown",
               format.args = list(digits = 3))
```

**Note:**
- `avg_total_wear_time` = Average total wear time since enrollment across all participants
- `prop_avg_total_wear_time` = Proportion of average total wear time since enrollment across all participants

## Code used 

```{r provenance, echo=FALSE, results='asis'}
this_file_path <- "dashboards/fitbit-dailydata-metrics/fitbit-dailydata-metrics.Rmd"

latest_file_commit <- 
  gh::gh("/repos/:owner/:repo/commits", 
         owner = "pranavanba", 
         repo = "RECOVER-MHDR-Analysis", 
         path = this_file_path)[[1]]$commit$url %>% 
  {gsub("https://api.github.com/repos/", "https://github.com/", .)} %>% {gsub("/git/commits/", "/blob/", .)} %>% glue::glue("/{this_file_path}")

cat("[GitHub Code](", latest_file_commit, ")")
```


```{r knit into synapse, eval=FALSE, include=FALSE}
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login(authToken = Sys.getenv("SYNAPSE_AUTH_TOKEN"))

### Please install v1.28 of reticulate, as this is the needed version for synapser
### devtools::install_version("reticulate", version = "1.28", repos = "http://cran.us.r-project.org")
DASHBOARD_FOLDER_SYNID <- "syn55256828"
FOLDER_NAME <- "Fitbit DailyData Metrics"

knit2synapse:::createAndKnitToFolderEntityClient(
  file = "dashboards/fitbit-dailydata-metrics/fitbit-dailydata-metrics.Rmd",
  parentId = DASHBOARD_FOLDER_SYNID,
  folderName = FOLDER_NAME)
```
