---
title: "Sleep Dashboard"
output: html_document
chunk_output_type: console
---

```{r knit into synapse, eval=FALSE, include=FALSE}
#### Block with parameters (archive version, synapse parentId and synapse folder name) for knit2Synapse
library(synapser)
library(knit2synapse)
# devtools::install_github("jgockley62/knit2synapse")
library(githubr)
# devtools::install_github("brian-bot/githubr")

synapser::synLogin()

######### change knit2synapse to Jake's version

#### ARCHIVE VERSION
ARCHIVE_VERSION <- '2024-06-13'  ## UPDATE archive version here

#### GitHub Token
# gtToken = "<YOUR GITHUB PERSONAL TOKEN>"

## New lines for calling synapseclient
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login() # is fails use syn_temp$login(authToken = <yourPAT>)
# get your PAT at "https://www.synapse.org/#!PersonalAccessTokens:"

### Note the new function being called from knit2synapse
### Please install this version of knit2synapse
### devtools::install_github("jgockley62/knit2synapse")

### Please install v1.28 of reticulate, as this is the needed version for synapser
### devtools::install_version("reticulate", version = "1.28", repos = "http://cran.us.r-project.org")
# knit2synapse:::createAndKnitToFolderEntityClient(file = "dashboard_sleep.Rmd",
#                                                  parentId = "syn61348473",
#                                                  folderName = 'Sleep')
knit2synapse::knitfile2synapse(file = "dashboard_sleep.Rmd",
                               owner = "syn51105296",
                               parentWikiId = '627716',
                               wikiName = 'Sleep',
                               overwrite = TRUE)
```

```{r required libraries, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
########
# Required Libraries
########
library(synapser)
library(tidyverse)
library(arrow)
library(lubridate)
library(knitr)
```

```{r required functions, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
## Custom functions for data processing
summarizeData <- function(pDat){
  
  # print(nrow(pDat))
  
  pDat_dataset <- paste0(pDat$dataset %>% unique(), collapse = ',')
  
  pDat_return <- pDat %>% 
    dplyr::select(-dataset) %>% 
    unique() %>% 
    dplyr::mutate(dataset = pDat_dataset)
  
  return(pDat_return)
  
}

```

```{r setup and download, include=FALSE, warning=FALSE, message=FALSE}
############################
## Get Sleep data
############################
## Set up Token access
synapser::synLogin()
sts_token <- synapser::synGetStsStorageToken(entity = 'syn52506069', # sts enabled destination folder
                                             permission = 'read_only',   # request a read only token
                                             output_format = 'json')

s3_external <- arrow::S3FileSystem$create(access_key = sts_token$accessKeyId,
                                          secret_key = sts_token$secretAccessKey,
                                          session_token = sts_token$sessionToken,
                                          region="us-east-1")

## Get list of datasets in the S3 bucket
base_s3_uri_external <- paste0(sts_token$bucket, "/", sts_token$baseKey,'/',ARCHIVE_VERSION)
parquet_datasets_external <- s3_external$GetFileInfo(arrow::FileSelector$create(base_s3_uri_external, recursive=F))

## Get all valid datasets
i <- 0
valid_paths <- character()
for (dataset in parquet_datasets_external) {
  if (grepl('recover-main-project/main/archive/', dataset$path, perl = T, ignore.case = T)) {
    i <- i+1
    cat(i)
    cat(":", dataset$path, "\n")
    valid_paths <- c(valid_paths, dataset$path)
  }
}

## Get dataset type (for eg., dataset_enrolledparticipants)
valid_paths_ext_df <- valid_paths %>% 
  as.data.frame() %>% 
  `colnames<-`('parquet_path_external') %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(datasetType = str_split(parquet_path_external,'/')[[1]][5]) %>%
  dplyr::ungroup()

#### Get the sleep data in
dataset_path <- valid_paths[grepl('fitbitsleeplogs',valid_paths)][1]
fitbit_sleeplogs <-  arrow::open_dataset(s3_external$path(as.character(dataset_path))) %>% dplyr::collect()

dataset_path <- valid_paths[grepl('enrolled',valid_paths)][1]
enrolledparticipants <-  arrow::open_dataset(s3_external$path(as.character(dataset_path))) %>% dplyr::collect()
```



```{r needed metrics, include=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
##############
### fitbit_sleeplogs
## Summarizations needed:
## (Sleep - Classic or stages)
#   1. Number of Sleep Records
#   2. Number of Sleep participants
#   3. Number of Sleep days
#   4. Average Number of Sleep days per participant
#   5. Percentage of Sleep days since enrollment
## (Sleep - Stages)
#   6. Number of Sleep Stages participants
#   7. Number of Sleep Stages days
#   8. Average Number of Sleep Stages days per participant
#   9. Percentage of Sleep Stages days since enrollment
#   10. Proportion of days with naps (given they had sleep data on a given day)
#   11. Distribution of lengths of non-isMainSleep
##############
```

### Number of records

```{r Number of records, echo=FALSE, warning=FALSE, message=FALSE}
# 1 
number_of_records <- fitbit_sleeplogs %>% 
  dplyr::group_by(Type,IsMainSleep) %>% 
  dplyr::count() %>% 
  dplyr::full_join(data.frame(Type = 'Total',
                              IsMainSleep = '--',
                              n = nrow(fitbit_sleeplogs)))

kable(number_of_records)
```

### Number of participants
```{r Number of participants, echo=FALSE, warning=FALSE, message=FALSE}
# 2 and 6
number_of_sleep_participants <- fitbit_sleeplogs %>% 
  dplyr::select(ParticipantIdentifier, Type) %>% 
  unique() %>% 
  dplyr::left_join(fitbit_sleeplogs %>% 
                     dplyr::select(ParticipantIdentifier, Type) %>% 
                     unique() %>% 
                     dplyr::group_by(ParticipantIdentifier) %>%
                     dplyr::count() %>% 
                     dplyr::ungroup()
  ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(newType = ifelse(n==2,'classic and stages',Type)) %>% 
  dplyr::ungroup() %>% 
  dplyr::select(-Type) %>% 
  unique() %>% 
  dplyr::group_by(newType) %>% 
  dplyr::count() %>% 
  dplyr::ungroup()

number_of_sleep_participants <- rbind(number_of_sleep_participants, data.frame('newType' = 'Total', 'n' = sum(number_of_sleep_participants$n)))

number_of_sleep_participants <- number_of_sleep_participants %>% 
  dplyr::rename(type = newType)

kable(number_of_sleep_participants)
```

### Number of participants (IsMainSleep = TRUE)
```{r Number of participants ismainsleep, echo=FALSE, warning=FALSE, message=FALSE}
# 2 and 6
number_of_sleep_participants <- fitbit_sleeplogs %>% 
  dplyr::filter(IsMainSleep == 'True') %>% ######## Filter IsMainSleep = TRUE
  dplyr::select(ParticipantIdentifier, Type) %>% 
  unique() %>% 
  dplyr::left_join(fitbit_sleeplogs %>% 
                     dplyr::select(ParticipantIdentifier, Type) %>% 
                     unique() %>% 
                     dplyr::group_by(ParticipantIdentifier) %>%
                     dplyr::count() %>% 
                     dplyr::ungroup()
  ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(newType = ifelse(n==2,'classic and stages',Type)) %>% 
  dplyr::ungroup() %>% 
  dplyr::select(-Type) %>% 
  unique() %>% 
  dplyr::group_by(newType) %>% 
  dplyr::count() %>% 
  dplyr::ungroup()

number_of_sleep_participants <- rbind(number_of_sleep_participants, data.frame('newType' = 'Total', 'n' = sum(number_of_sleep_participants$n)))

number_of_sleep_participants <- number_of_sleep_participants %>% 
  dplyr::rename(type = newType)

kable(number_of_sleep_participants)
```


### Number of Sleep days

Assuming that a record that is atleast 3 hrs long to be considered a sleep record. A day with atleast one sleep record is considered a sleep day
```{r Number of Sleep days, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}
# 3 and 7 (consider atleast 3 hrs for a sleep day)
number_of_sleep_days <- fitbit_sleeplogs %>% 
  dplyr::select(ParticipantIdentifier, StartDate, EndDate, Duration, Type) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(dayOfRecording= as.Date(StartDate),
                Duration = as.numeric(Duration)) %>% 
  dplyr::filter(Duration >= 180) %>% # atleast 180min ie 3Hrs to be considered a sleep day/record
  dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, dayOfRecording, Type) %>%
  unique() 

number_of_sleep_days <- number_of_sleep_days %>% 
  dplyr::left_join(number_of_sleep_days %>% 
                     dplyr::group_by(ParticipantIdentifier, dayOfRecording) %>% 
                     count()) %>% 
  dplyr::mutate(newType = ifelse(n==2, 'classic and stages', Type)) %>% 
  dplyr::select(-Type) %>% 
  unique() %>% 
  dplyr::group_by(ParticipantIdentifier, newType) %>% 
  count() %>% 
  dplyr::rename(Type = newType) %>% 
  dplyr::ungroup()

options(repr.plot.width = 9, repr.plot.height =6)
ggplot2::ggplot(data = number_of_sleep_days, aes(x = n))+ geom_histogram() + xlab('Number of days with atleast one 3 hr record (log scale)') + ylab('Number of records') +
  theme_minimal() + facet_wrap(~Type) + scale_x_log10()

```

### Number of Sleep days (IsMainSleep = TRUE)

Assuming that a record that is atleast 3 hrs long to be considered a sleep record. A day with atleast one sleep record is considered a sleep day
```{r Number of Sleep days ismainsleep, echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}
# 3 and 7 (consider atleast 3 hrs for a sleep day)
number_of_sleep_days <- fitbit_sleeplogs %>% 
  dplyr::filter(IsMainSleep == 'True') %>% ######## Filter IsMainSleep = TRUE
  dplyr::select(ParticipantIdentifier, StartDate, EndDate, Duration, Type) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(dayOfRecording= as.Date(StartDate),
                Duration = as.numeric(Duration)) %>% 
  dplyr::filter(Duration >= 180) %>% # atleast 180min ie 3Hrs to be considered a sleep day/record
  dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, dayOfRecording, Type) %>%
  unique() 

number_of_sleep_days <- number_of_sleep_days %>% 
  dplyr::left_join(number_of_sleep_days %>% 
                     dplyr::group_by(ParticipantIdentifier, dayOfRecording) %>% 
                     count()) %>% 
  dplyr::mutate(newType = ifelse(n==2, 'classic and stages', Type)) %>% 
  dplyr::select(-Type) %>% 
  unique() %>% 
  dplyr::group_by(ParticipantIdentifier, newType) %>% 
  count() %>% 
  dplyr::rename(Type = newType) %>% 
  dplyr::ungroup()

options(repr.plot.width = 9, repr.plot.height =6)
ggplot2::ggplot(data = number_of_sleep_days, aes(x = n))+ geom_histogram() + xlab('Number of days with atleast one 3 hr record (log scale)') + ylab('Number of records') +
  theme_minimal() + facet_wrap(~Type) + scale_x_log10()

```


### Average number of sleep days
A day might have both classic and stages Type sleep records for a given participant. We are counting both in the averages below

```{r Avg number of sleep days, echo=FALSE, warning=FALSE, message=FALSE}
# 4 and 8
avg_number_of_sleep_days <- fitbit_sleeplogs %>% 
  dplyr::select(ParticipantIdentifier, StartDate, EndDate, Duration, Type) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(dayOfRecording= as.Date(StartDate),
                Duration = as.numeric(Duration)) %>% 
  dplyr::filter(Duration >= 180) %>% # atleast 180min ie 3Hrs to be considered a sleep day/record
  dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, dayOfRecording, Type) %>%
  unique() %>% 
  dplyr::group_by(ParticipantIdentifier, Type) %>% 
  dplyr::count() %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = mean(n),
                   median = median(n))

kable(avg_number_of_sleep_days)
```

### Average number of sleep days (IsMainSleep = TRUE)
A day might have both classic and stages Type sleep records for a given participant. We are counting both in the averages below

```{r Avg number of sleep days ismainsleep, echo=FALSE, warning=FALSE, message=FALSE}
# 4 and 8
avg_number_of_sleep_days <- fitbit_sleeplogs %>% 
  dplyr::filter(IsMainSleep == 'True') %>% ######## Filter IsMainSleep = TRUE
  dplyr::select(ParticipantIdentifier, StartDate, EndDate, Duration, Type) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(dayOfRecording= as.Date(StartDate),
                Duration = as.numeric(Duration)) %>% 
  dplyr::filter(Duration >= 180) %>% # atleast 180min ie 3Hrs to be considered a sleep day/record
  dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, dayOfRecording, Type) %>%
  unique() %>% 
  dplyr::group_by(ParticipantIdentifier, Type) %>% 
  dplyr::count() %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = mean(n),
                   median = median(n))

kable(avg_number_of_sleep_days)
```


### Percentage of sleep days since enrollment
```{r percentage of sleep days since enrollment,  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}
# 5 (Propotion of sleep days since enrollment)
sleep_days_since_enrollment <- fitbit_sleeplogs %>% 
  dplyr::left_join(enrolledparticipants %>% 
                     dplyr::select(ParticipantIdentifier, EnrollmentDate) %>% 
                     dplyr::mutate(days_enrolled = lubridate::days(Sys.Date() - as.Date(EnrollmentDate)))) %>% 
  dplyr::rowwise() %>% 
  dplyr::filter(StartDate >= EnrollmentDate) %>%  # records after enrollment
  dplyr::rowwise() %>% 
  dplyr::mutate(dayOfRecording= as.Date(StartDate),
                Duration = as.numeric(Duration)) %>% 
  dplyr::filter(Duration >= 180) %>% # atleast 180min ie 3Hrs to be considered a sleep day/record
  dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, dayOfRecording, days_enrolled, Type) %>%
  unique() %>% 
  dplyr::group_by(ParticipantIdentifier, days_enrolled, Type) %>% 
  count() %>%
  dplyr::ungroup() %>% 
  dplyr::rename(ndays_after_enrollment = n) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(percentage_sleep_days_post_enroll = 100*ndays_after_enrollment/lubridate::day(days_enrolled)) %>% 
  dplyr::ungroup()

options(repr.plot.width = 8, repr.plot.height =6)
ggplot2::ggplot(data = sleep_days_since_enrollment, aes(x = percentage_sleep_days_post_enroll))+ geom_histogram() + xlab('Percentage of Sleep days Since enrollment') + ylab('Number of records') + facet_wrap(~Type)+
  theme_minimal()

mean_percentage_sleep_days_since_enrollment <- sleep_days_since_enrollment %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = mean(percentage_sleep_days_post_enroll),
                   median = median(percentage_sleep_days_post_enroll))
kable(mean_percentage_sleep_days_since_enrollment)
```

### Average number of sleep days after enrollment
A day might have both classic and stages Type sleep records for a given participant. We are counting both in the averages below

```{r Avg number of sleep days after enrollment, echo=FALSE, warning=FALSE, message=FALSE}
# 4 and 8
avg_number_of_sleep_days_enrollment <- sleep_days_since_enrollment %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = mean(ndays_after_enrollment),
                   median = median(ndays_after_enrollment))

kable(avg_number_of_sleep_days_enrollment)
```


### Percentage of sleep days since enrollment (IsMainSleep = TRUE)
```{r percentage of sleep days since enrollment ismainsleep,  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}
# 5 (Propotion of sleep days since enrollment)
sleep_days_since_enrollment <- fitbit_sleeplogs %>% 
  dplyr::filter(IsMainSleep == 'True') %>% 
  dplyr::left_join(enrolledparticipants %>% 
                     dplyr::select(ParticipantIdentifier, EnrollmentDate) %>% 
                     dplyr::mutate(days_enrolled = lubridate::days(Sys.Date() - as.Date(EnrollmentDate)))) %>% 
  dplyr::rowwise() %>% 
  dplyr::filter(StartDate >= EnrollmentDate) %>%  # records after enrollment
  dplyr::rowwise() %>% 
  dplyr::mutate(dayOfRecording= as.Date(StartDate),
                Duration = as.numeric(Duration)) %>% 
  dplyr::filter(Duration >= 180) %>% # atleast 180min ie 3Hrs to be considered a sleep day/record
  dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, dayOfRecording, days_enrolled, Type) %>%
  unique() %>% 
  dplyr::group_by(ParticipantIdentifier, days_enrolled, Type) %>% 
  count() %>%
  dplyr::ungroup() %>% 
  dplyr::rename(ndays_after_enrollment = n) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(percentage_sleep_days_post_enroll = 100*ndays_after_enrollment/lubridate::day(days_enrolled)) %>% 
  dplyr::ungroup()

options(repr.plot.width = 8, repr.plot.height =6)
ggplot2::ggplot(data = sleep_days_since_enrollment, aes(x = percentage_sleep_days_post_enroll))+ geom_histogram() + xlab('Percentage of Sleep days Since enrollment') + ylab('Number of records') + facet_wrap(~Type)+
  theme_minimal()

mean_percentage_sleep_days_since_enrollment <- sleep_days_since_enrollment %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = mean(percentage_sleep_days_post_enroll),
                   median = median(percentage_sleep_days_post_enroll))
kable(mean_percentage_sleep_days_since_enrollment)
```


### Average number of sleep days after enrollment (IsMainSleep = TRUE)
A day might have both classic and stages Type sleep records for a given participant. We are counting both in the averages below

```{r Avg number of sleep days after enrollment ismainsleep, echo=FALSE, warning=FALSE, message=FALSE}
# 4 and 8
avg_number_of_sleep_days_enrollment <- sleep_days_since_enrollment %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = mean(ndays_after_enrollment),
                   median = median(ndays_after_enrollment))

kable(avg_number_of_sleep_days_enrollment)
```

```{r Summarize data for analysis and plots,  echo=FALSE, warning=FALSE, message=FALSE}
############
## Summary of data
############
####### SLEEP
sleep_summary <- fitbit_sleeplogs %>% 
  dplyr::select(ParticipantIdentifier, StartDate, EndDate) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(Date = as.Date(StartDate) %>% as.character()) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(dataset = 'fitbitsleeplogs')

####### SLEEP(IsMainSleep)
sleep_summary_ismainsleep <- fitbit_sleeplogs %>% 
  dplyr::filter(IsMainSleep == 'True') %>% ######## Filter IsMainSleep = TRUE
  dplyr::select(ParticipantIdentifier, StartDate, EndDate) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(Date = as.Date(StartDate) %>% as.character()) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(dataset = 'fitbitsleeplogs(IsMainSleep)')

####### Other Fitbit Measures
####### 
dataset_path <- valid_paths[grepl('activitylogs',valid_paths)][1]
fitbit_data <-  arrow::open_dataset(s3_external$path(as.character(dataset_path))) 
activitylogs_summary <- fitbit_data %>% 
  dplyr::select(ParticipantIdentifier, StartDate, EndDate) %>% 
  # dplyr::rowwise() %>% 
  # dplyr::mutate(Date = as.character(as.Date(StartDate))) %>% 
  # dplyr::ungroup() %>% 
  dplyr::mutate(dataset = 'activitylogs') %>%
  dplyr::collect()
activitylogs_summary$Date = as.character(as.Date(activitylogs_summary$StartDate))

dataset_path <- valid_paths[grepl('dailydata',valid_paths)][1]
fitbit_data <-  arrow::open_dataset(s3_external$path(as.character(dataset_path))) 
dailydata_summary <- fitbit_data %>% 
  # dplyr::rowwise() %>% 
  # dplyr::mutate(Date = as.character(as.Date(Date))) %>% 
  # dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, Date) %>% 
  dplyr::mutate(dataset = 'dailydata')%>%
  dplyr::collect()

dailydata_summary$Date = as.character(as.Date(dailydata_summary$Date))

dataset_path <- valid_paths[grepl('fitbitrestingheartrates',valid_paths)][1]
fitbit_data <-  arrow::open_dataset(s3_external$path(as.character(dataset_path))) 
restingHR_summary <- fitbit_data %>% 
  # dplyr::rowwise() %>% 
  # dplyr::mutate(Date = as.character(as.Date(Date))) %>% 
  # dplyr::ungroup() %>% 
  dplyr::select(ParticipantIdentifier, Date) %>% 
  dplyr::mutate(dataset = 'restingHR')%>%
  dplyr::collect()

restingHR_summary$Date = as.character(as.Date(restingHR_summary$Date))

### merge em all
aa <- sleep_summary %>% 
  dplyr::full_join(sleep_summary_ismainsleep) %>% 
  dplyr::full_join(activitylogs_summary) %>% 
  dplyr::full_join(restingHR_summary) %>% 
  dplyr::full_join(dailydata_summary) %>% 
  dplyr::select(ParticipantIdentifier,
                Date,
                dataset) %>% 
  unique() %>% 
  na.omit() %>% 
  dplyr::group_by(ParticipantIdentifier, Date) %>% 
  do(summarizeData(.)) %>% 
  dplyr::mutate(dailydata = ifelse(grepl('dailydata',dataset),TRUE,FALSE)) %>% 
  dplyr::mutate(activitylogs = ifelse(grepl('activitylogs',dataset),TRUE,FALSE)) %>% 
  dplyr::mutate(restingHR = ifelse(grepl('restingHR',dataset),TRUE,FALSE)) %>% 
  dplyr::mutate(fitbitsleeplogs = ifelse(grepl('fitbitsleeplogs',dataset),TRUE,FALSE)) %>% 
  dplyr::mutate(fitbitsleeplogs_isMainSleep = ifelse(grepl('IsMainSleep',dataset),TRUE,FALSE)) %>% 
  dplyr::mutate(otherData = ifelse(dailydata || activitylogs || restingHR, TRUE, FALSE)) %>% 
  ungroup() %>% 
  dplyr::left_join(enrolledparticipants %>% 
                     dplyr::select(ParticipantIdentifier, EnrollmentDate) %>% 
                     dplyr::mutate(days_enrolled = lubridate::days(Sys.Date() - as.Date(EnrollmentDate)))) %>% 
  dplyr::filter(Date >= EnrollmentDate)   # records after enrollment

aa$row <- rownames(aa)

aa3 <- aa %>% 
  dplyr::select(row, dailydata, activitylogs, restingHR, fitbitsleeplogs, fitbitsleeplogs_isMainSleep, otherData) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(dailydata = as.integer(dailydata),
                activitylogs = as.integer(activitylogs),
                restingHR = as.integer(restingHR),
                fitbitsleeplogs = as.integer(fitbitsleeplogs),
                fitbitsleeplogs_isMainSleep = as.integer(fitbitsleeplogs_isMainSleep),
                otherData = as.integer(otherData)) %>% 
  ungroup() 
```

### Plots of Fitbit Sleep data vs other forms of Fitbit Data (dailydata, restingHR, activitylogs, sleeplogs)
For a given participant, we check for each day if have a record for the various data types. Each record is a day for a participant. So the intersection size is the number of "day-participant" instances that we have data, for that specific data type. 

```{r sleep vs dailydata-restingHR-activitylogs,  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}
library(UpSetR)
upset(as.data.frame(aa3),
      sets = c('dailydata','restingHR', 'activitylogs', 'fitbitsleeplogs'),
      order.by = "freq", text.scale = 2)
```

```{r sleep vs other data as a whole,  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}

upset(as.data.frame(aa3),
      sets = c('otherData', 'fitbitsleeplogs'),
      order.by = "freq", text.scale = 2)
```

### Plots of Fitbit Sleep data(IsMainSleep) vs other forms of Fitbit Data (dailydata, restingHR, activitylogs, sleeplogs)
For a given participant, we check for each day if have a record for the various data types. Each record is a day for a participant. So the intersection size is the number of "day-participant" instances that we have data, for that specific data type. 

```{r sleep vs dailydata-restingHR-activitylogs isMainSleep,  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}
library(UpSetR)
upset(as.data.frame(aa3),
      sets = c('dailydata','restingHR', 'activitylogs', 'fitbitsleeplogs_isMainSleep'),
      order.by = "freq", text.scale = 2)
```

```{r sleep vs other data as a whole isMainSleep,  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width=20}

upset(as.data.frame(aa3),
      sets = c('otherData', 'fitbitsleeplogs_isMainSleep'),
      order.by = "freq", text.scale = 2)
```


## Naps Analyses

`isMainSleep == False`

### Percentage of Sleep Days with Naps Since Enrollment

```{r}
nap_days_since_enrollment <- 
  fitbit_sleeplogs %>% 
  filter(IsMainSleep == 'False') %>% 
  left_join(
    enrolledparticipants %>% 
      select(ParticipantIdentifier, EnrollmentDate) %>% 
      mutate(days_enrolled = lubridate::days(Sys.Date() - as.Date(EnrollmentDate))),
    by = join_by(ParticipantIdentifier)
  ) %>% 
  filter(as.Date(StartDate) >= as.Date(EnrollmentDate)) %>%  # records after enrollment
  mutate(dayOfRecording= as.Date(StartDate),
                Duration = as.numeric(Duration)) %>% 
  # filter(Duration >= 10.8e6) %>% # atleast 180min ie 3Hrs to be considered a sleep day/record
  select(ParticipantIdentifier, dayOfRecording, days_enrolled, Type) %>%
  unique() %>% 
  group_by(ParticipantIdentifier, days_enrolled, Type) %>% 
  count() %>%
  ungroup() %>% 
  rename(ndays_after_enrollment = n) %>% 
  mutate(percentage_nap_days_post_enroll = 100*ndays_after_enrollment/lubridate::day(days_enrolled)) %>% 
  ungroup()

options(repr.plot.width = 8, repr.plot.height =6)
ggplot2::ggplot(data = nap_days_since_enrollment, 
                aes(x = percentage_nap_days_post_enroll)) + 
  geom_histogram(binwidth = 1) + 
  labs(x = "Percentage of Nap Days Since Enrollment",
       y = "Frequency")+
  facet_wrap("Type", dir = "v") +
  theme_minimal()

mean_percentage_nap_days_since_enrollment <- 
  nap_days_since_enrollment %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = round(mean(percentage_nap_days_post_enroll), 3),
                   median = round(median(percentage_nap_days_post_enroll), 3))

kable(mean_percentage_nap_days_since_enrollment)
```

### Average Number of Sleep Days with Naps Since Enrollment

```{r}
avg_number_of_nap_days_enrollment <- 
  nap_days_since_enrollment %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = round(mean(ndays_after_enrollment), 1),
                   median = round(median(ndays_after_enrollment), 1))

kable(avg_number_of_nap_days_enrollment)
```

### Distribution of Nap Durations Since Enrollment

*Lengths of non-isMainSleep Sleep Episodes in Minutes*

```{r}
nap_durations <- 
  fitbit_sleeplogs %>% 
  filter(IsMainSleep=="False") %>% 
  left_join(
    enrolledparticipants %>% 
      select(ParticipantIdentifier, EnrollmentDate) %>% 
      mutate(days_enrolled = lubridate::days(Sys.Date() - as.Date(EnrollmentDate))),
    by = join_by(ParticipantIdentifier)
  ) %>% 
  mutate(StartDate = as.Date(StartDate),
         EnrollmentDate = as.Date(EnrollmentDate),
         day = weekdays(StartDate),
         weekday = ifelse(day=="Saturday" | day=="Sunday", "Weekend", "Weekday")) %>% 
  filter(StartDate >= EnrollmentDate) %>% 
  select(StartDate, weekday, Type, Duration) %>% 
  mutate(Duration = as.numeric(Duration)/60000)

options(repr.plot.width = 8, repr.plot.height =6)

ggplot(nap_durations, aes(x = Duration, fill = Type)) +
  geom_histogram(binwidth = 10, position = "dodge") +
  labs(x = "Nap Duration (minutes)", 
       y = "Frequency") +
  scale_fill_grey() +
  scale_x_continuous(breaks = seq(0, max(nap_durations$Duration), 200)) +
  # facet_wrap("weekday") +
  # facet_grid(vars(Type), vars(weekday)) +
  theme_minimal()

ggplot(nap_durations, aes(x = Type, y = Duration)) +
  geom_violin(fill = "darkgray", alpha = 0.5, trim = TRUE) +
  labs(x = "Type",
       y = "Nap Duration (minutes)") +
  theme_minimal() +
  coord_flip() +
  geom_boxplot(width = 0.1, outliers = TRUE, outlier.size = 0.75) +
  scale_y_continuous(breaks = seq(0, max(nap_durations$Duration), 200))
```

### Average Nap Duration Since Enrollment

```{r}
mean_nap_duration_since_enrollment <- 
  nap_durations %>% 
  dplyr::group_by(Type) %>% 
  dplyr::summarise(mean = round(mean(Duration), 1),
                   median = round(median(Duration), 1))

kable(mean_nap_duration_since_enrollment)
```

### Code used 
```{r get provenance, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
### Commenting out - doesnt work across users without 
# githubr::setGithubToken(gtToken)
# thisFileName <- "dashboards/Sleep/dashboard_sleep.Rmd" # location of file inside github repo
# thisRepo <- githubr::getRepo(repository = "itismeghasyam/RECOVER-MHDR-Analysis",
#                     ref="branch",
#                     refName="main")
# thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=thisFileName)
```

```{r print provenance, echo=FALSE, results='asis'}
# http_address <- glue::glue("{thisFile}")
http_address <- 'https://github.com/itismeghasyam/RECOVER-MHDR-Analysis/blob/main/dashboards/Sleep/dashboard_sleep.Rmd'
cat("[GitHub Code](", http_address, ")")
```
