---
title: "Check Missingness"
output: html_document
date: "`r base::date()`"
chunk_output_type: console
---

```{r, eval=F, include=F}
token=as.character(read.table("token_lyl"))
## New lines for calling synapseclient
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login(authToken=token) 


### Note the new function being called from knit2synapse
### Please install this version of knit2synapse
### devtools::install_github("jgockley62/knit2synapse")
### Please update/downgrade your reticulate package version to 1.28 if knitting fails
### devtools::install_version("reticulate", version = "1.28", repos = "http://cran.us.r-project.org")
library(synapser)
library(knit2synapse)
synapser::synLogin(authToken=token)
knit2synapse:::createAndKnitToFolderEntityClient(file = "Checkmissingness.Rmd",
                                          parentId = "syn52566784",
                                          folderName = "Check_Missingness_Dashboard")

```


```{r load packages, include=F}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(synapser)
library(arrow)
library(knitr)
library(tidyverse)
library(psych)
source("HandyMissingDataFunctions.R")
token=as.character(read.table("token_lyl"))
synapser::synLogin(authToken=token)

ARCHIVE_VERSION <- '2023-11-10'
archivefolder_id = 'syn52506069'  
sts_token <- synapser::synGetStsStorageToken(entity = archivefolder_id, # sts enabled destination folder
                                             permission = 'read_only',   # request a read only token
                                             output_format = 'json')

s3_external <- arrow::S3FileSystem$create(access_key = sts_token$accessKeyId,
                                          secret_key = sts_token$secretAccessKey,
                                          session_token = sts_token$sessionToken,
                                          region="us-east-1")
base_s3_uri_external <- paste0(sts_token$bucket, "/", sts_token$baseKey,'/',ARCHIVE_VERSION)
parquet_datasets_external <- s3_external$GetFileInfo(arrow::FileSelector$create(base_s3_uri_external, recursive=F))

## Get all valid datasets
i <- 0
valid_paths <- character()
for (dataset in parquet_datasets_external) {
  #if(!grepl('.*owner.*', dataset$path, perl = T, ignore.case = T)){
  if (grepl('recover-main-project/main/archive/', dataset$path, perl = T, ignore.case = T)) {
    i <- i+1
    cat(i)
    cat(":", dataset$path, "\n")
    valid_paths <- c(valid_paths, dataset$path)
  }
}

readdata = function(file_num){
  dataset_path <- valid_paths[file_num]
  df <- arrow::open_dataset(s3_external$path(dataset_path)) %>% 
    dplyr::collect()
  return(df)
}

enrolledparticipants = readdata(1)
fitbit_activitylogs = readdata(4)
fitbit_daily = readdata(5)
fitbit_devices = readdata(6)
fitbit_sleeplogs = readdata(9)

```


## Fitbit Devices

Number of participants wearing Fitbit devices (based on `dataset_fitbitdailydata`):

```{r}
ID_daily = unique(fitbit_daily$ParticipantIdentifier)
print(length(ID_daily))
```

Number of participants wearing Fitbit devices (based on `dataset_fitbitdevices`):

```{r}
ID_devices = unique(fitbit_devices$ParticipantIdentifier)
# number of participants wearing fitbit devices
print(length(ID_devices))
```

```{r}
sub_enrolled=enrolledparticipants
sub_enrolled$Sense2=rep(0,nrow(sub_enrolled))
sub_enrolled$Charge5=rep(0,nrow(sub_enrolled))
sub_enrolled$onlyordered=rep(0,nrow(sub_enrolled))
numofdevices=c()

for(i in 1:length(ID_devices)){
  deviceinfo = unique(fitbit_devices[fitbit_devices$ParticipantIdentifier==ID_devices[i],"Device"]$Device)
  numofdevices[i] = length(deviceinfo)
  if("Sense 2" %in% deviceinfo){
    sub_enrolled[sub_enrolled$ParticipantIdentifier==ID_devices[i],"Sense2"] = 1 
  }
  if("Charge 5" %in% deviceinfo){
    sub_enrolled[sub_enrolled$ParticipantIdentifier==ID_devices[i],"Charge5"] = 1 
  }
  if(length(deviceinfo)-sum(deviceinfo%in%c("Sense 2", "Charge 5"))==0){
    sub_enrolled[sub_enrolled$ParticipantIdentifier==ID_devices[i],"onlyordered"] = 1
  }
}

```


Number of participants only wearing only Fitbit Sense 2 and/or Charge 5:

```{r}
# IDs with ONLY Sense 2 and/or Charge 5
ID_twodevices = sub_enrolled$ParticipantIdentifier[sub_enrolled$onlyordered==1]
length(ID_twodevices)
```

## About COVID Infection Dates

Number of participants who reported infection dates:

```{r}
as.numeric(table(is.na(enrolledparticipants$CustomFields_InfectionFirstReportedDate))[1])
```


Number of participants who reported infection dates and wore only Fitbit Charge 5 or Sense 2:

```{r}
as.numeric(table(!is.na(sub_enrolled$CustomFields_InfectionFirstReportedDate) & sub_enrolled$onlyordered==1)[2]) 
```

Number of participants who were infected more than once:

```{r}
as.numeric(table(enrolledparticipants$CustomFields_InfectionsReported>1)[2])
```

## Subset Data Based on New Definitions of Start/End Dates

Number of participants if we define the start date as the first date with non-zero values on `HeartRateIntradayMinuteCount` after the enrollment date:

```{r}
fitbit_daily$Date2 = as.Date(fitbit_daily$Date)
new2_fitbit_daily = NULL # use non-zero start/end date

for(i in 1:length(ID_daily)){
  enrollmentdate = as.Date(as.character(enrolledparticipants[enrolledparticipants$ParticipantIdentifier==ID_daily[i],"EnrollmentDate"]))
  tmp_daily = fitbit_daily%>%
    filter(ParticipantIdentifier==ID_daily[i] & Date2>=enrollmentdate)%>%
    arrange(Date2)
  rowindex = which(tmp_daily$HeartRateIntradayMinuteCount!=0)
  if(length(rowindex)>0){
    data2 = tmp_daily[rowindex[1]:rowindex[length(rowindex)],]
  }else{
    data2 = NULL
  }
  new2_fitbit_daily = rbind(new2_fitbit_daily, data2)
}


print(length(unique(new2_fitbit_daily$ParticipantIdentifier)))

```

```{r}
# check start/end date in fitbit_daily
timerange_daily = fitbit_daily%>%
  group_by(ParticipantIdentifier)%>%
  summarise(start_daily = min(Date2), end_daily = max(Date2))

# check start/end date in fitbit_devices
fitbit_devices$Date2 = as.Date(fitbit_devices$Date)
timerange_v1 = fitbit_devices%>%
  group_by(ParticipantIdentifier)%>%
  summarise(start_v1 = min(Date2), end_v1 = max(Date2))

# check start/end date in new fitbit daily data (start date is defined above)
timerange_v2 = new2_fitbit_daily%>%
  group_by(ParticipantIdentifier)%>%
  summarise(start_v2 = min(Date2), end_v2 = max(Date2))

timerange = merge(timerange_daily,timerange_v1,by="ParticipantIdentifier",all.x=TRUE)
timerange = merge(timerange, timerange_v2, by="ParticipantIdentifier",all.x=TRUE)
timerange = merge(timerange, enrolledparticipants[,c("ParticipantIdentifier","EnrollmentDate",
                                                     "CustomFields_DevicesConnectedDate")], 
                  by = "ParticipantIdentifier",all.x=TRUE)

# if non-zero start date < device connected date, flag the participant as isBeforeRECOVER = 1
timerange$isBeforeRECOVER = ifelse(timerange$start_v2 < timerange$CustomFields_DevicesConnectedDate, 1, 0)


# check start/end date in fitbit_sleeplogs (generally match the non-zero state/end date)
fitbit_sleeplogs$StartDate2 = as.Date(fitbit_sleeplogs$StartDate)
timerange_sleep = fitbit_sleeplogs%>%
  group_by(ParticipantIdentifier)%>%
  summarise(start_sleep = min(StartDate2), end_sleep = max(StartDate2))
timerange = merge(timerange, timerange_sleep, by="ParticipantIdentifier",all.x=TRUE)

# check start/end date in fitbit_activitylogs (generally match the non-zero state/end date)
fitbit_activitylogs$StartDate2 = as.Date(fitbit_activitylogs$StartDate)
timerange_activity = fitbit_activitylogs%>%
  group_by(ParticipantIdentifier)%>%
  summarise(start_activity = min(StartDate2), end_activity = max(StartDate2))
timerange = merge(timerange, timerange_activity, by="ParticipantIdentifier",all.x=TRUE)

```

## Sleep Metrics

```{r}
# Sleeplogs: "Duration", "Efficiency", "TimeInBed", "Type" (classic or stages)
ID_sleep = unique(fitbit_sleeplogs$ParticipantIdentifier)
#table(ID_sleep%in%ID_twodevices) 

# select the maximum sleep duration within a day for a participant
fitbit_sleeplogs$Date2 = as.Date(fitbit_sleeplogs$EndDate)
dat_sleep_all = fitbit_sleeplogs%>%
  group_by(ParticipantIdentifier, Date2)%>%
  filter(Duration == max(as.numeric(Duration)))%>%
  rename("Duration_Sleeplogs" = "Duration",
         "Efficiency_Sleeplogs" = "Efficiency",
         "TimeInBed_Sleeplogs" = "TimeInBed")
dat_sleep_classic = fitbit_sleeplogs%>%
  filter(Type == "classic")%>%
  group_by(ParticipantIdentifier, Date2)%>%
  filter(Duration == max(as.numeric(Duration)))%>%
  rename("Duration_Sleeplogs_Classic" = "Duration",
         "Efficiency_Sleeplogs_Classic" = "Efficiency",
         "TimeInBed_Sleeplogs_Classic" = "TimeInBed")
dat_sleep_stages = fitbit_sleeplogs%>%
  filter(Type == "stages")%>%
  group_by(ParticipantIdentifier, Date2)%>%
  filter(Duration == max(as.numeric(Duration)))%>%
  rename("Duration_Sleeplogs_Stages" = "Duration",
         "Efficiency_Sleeplogs_Stages" = "Efficiency",
         "TimeInBed_Sleeplogs_Stages" = "TimeInBed")


```


## Activity Metrics

```{r}
# Activitylogs: "SedentaryMinutes", "LightlyMinutes", "FairlyMinutes", "VeryMinutes", "Steps"
# fitbitdaily: Tracker_MinutesSedentary, Tracker_MinutesLightlyActive, Tracker_MinutesFairlyActive, Tracker_MinutesVeryActive, Tracker_Steps
ID_activity = unique(fitbit_activitylogs$ParticipantIdentifier)
#table(ID_activity%in%ID_twodevices) 
#table(ID_activity%in%ID_sleep)

# select the total activity duration within a day for a participant
fitbit_activitylogs$Date2 = as.Date(fitbit_activitylogs$EndDate)
dat_activity = fitbit_activitylogs%>%
  group_by(ParticipantIdentifier, Date2)%>%
  summarise(Duration_Activitylogs = sum(as.numeric(Duration)),
            SedentaryMinutes_Activitylogs = sum(as.numeric(SedentaryMinutes)),
            LightlyMinutes_Activitylogs = sum(as.numeric(LightlyMinutes)),
            FairlyMinutes_Activitylogs = sum(as.numeric(FairlyMinutes)),
            VeryMinutes_Activitylogs = sum(as.numeric(VeryMinutes)),
            Steps_Activitylogs = sum(as.numeric(Steps))  )

```

## Histograms of Key Fitbit Measures

Plots are generated based on data with non-zero start dates.

```{r}
par(mfrow=c(3,2))

# check the distribution of HeartRateIntradayMinuteCount to get a sense of nonwearing time
#describe(as.numeric(new2_fitbit_daily$HeartRateIntradayMinuteCount))
hist(as.numeric(new2_fitbit_daily$HeartRateIntradayMinuteCount), main = "Histogram of HeartRateIntrdayMinuteCount", xlab="HeartRateIntrdayMinuteCount")

#describe(as.numeric(new2_fitbit_daily$RestingHeartRate))
hist(as.numeric(new2_fitbit_daily$RestingHeartRate), main = "Histogram of RestingHeartRate", xlab="RestingHeartRate")

#describe(as.numeric(new2_fitbit_daily$Steps))
hist(as.numeric(new2_fitbit_daily$Steps), main = "Histogram of Steps", xlab="Steps")

#describe(as.numeric(new2_fitbit_daily$SpO2_Avg))
hist(as.numeric(new2_fitbit_daily$SpO2_Avg), main = "Histogram of SpO2_Avg", xlab="SpO2_Avg")

#describe(as.numeric(new2_fitbit_daily$Hrv_DailyRmssd))
hist(as.numeric(new2_fitbit_daily$Hrv_DailyRmssd), main = "Histogram of Hrv_DailyRmssd", xlab="Hrv_DailyRmssd")
```


## Missing Data Metrics


### Overall Missingness in Fitbit Measures


#### Based on Participants Wearing Only Sense 2/Charge 5


```{r}
alldata  = merge(new2_fitbit_daily, dat_activity, by=c("ParticipantIdentifier","Date2"), all.x=TRUE)
alldata = merge(alldata, dat_sleep_all, by=c("ParticipantIdentifier","Date2"), all.x=TRUE)
alldata = merge(alldata, dat_sleep_classic[,c("ParticipantIdentifier","Date2","Duration_Sleeplogs_Classic", "Efficiency_Sleeplogs_Classic", "TimeInBed_Sleeplogs_Classic")], by=c("ParticipantIdentifier","Date2"), all.x=TRUE)
alldata = merge(alldata, dat_sleep_stages[,c("ParticipantIdentifier","Date2","Duration_Sleeplogs_Stages", "Efficiency_Sleeplogs_Stages", "TimeInBed_Sleeplogs_Stages")], by=c("ParticipantIdentifier","Date2"), all.x=TRUE)


#measures = c("ParticipantIdentifier","BodyBmi","BodyFat","BodyWeight","BreathingRate","Calories","CaloriesBMR","Distance","FoodCaloriesIn","HeartRateIntradayMinuteCount","Hrv_DailyRmssd","Hrv_DeepRmssd","MinutesFairlyActive","MinutesLightlyActive","MinutesSedentary","MinutesVeryActive","RestingHeartRate","SpO2_Avg","SpO2_Max","SpO2_Min","Steps","Elevation","Floors","Tracker_ActivityCalories","Tracker_Calories","Tracker_Distance","Tracker_Elevation","Tracker_Floors","Tracker_MinutesFairlyActive","Tracker_MinutesLightlyActive","Tracker_MinutesSedentary","Tracker_MinutesVeryActive","Tracker_Steps","Duration_Sleeplogs", "Efficiency_Sleeplogs", "TimeInBed_Sleeplogs","Duration_Sleeplogs_Classic", "Efficiency_Sleeplogs_Classic", "TimeInBed_Sleeplogs_Classic","Duration_Sleeplogs_Stages", "Efficiency_Sleeplogs_Stages", "TimeInBed_Sleeplogs_Stages","Duration_Activitylogs","SedentaryMinutes_Activitylogs", "LightlyMinutes_Activitylogs", "FairlyMinutes_Activitylogs", "VeryMinutes_Activitylogs", "Steps_Activitylogs")

measures = rev(c("Duration_Sleeplogs", "Efficiency_Sleeplogs", "TimeInBed_Sleeplogs",
             "Duration_Sleeplogs_Stages", "Efficiency_Sleeplogs_Stages", "TimeInBed_Sleeplogs_Stages",
             "Duration_Sleeplogs_Classic", "Efficiency_Sleeplogs_Classic", "TimeInBed_Sleeplogs_Classic",
             "HeartRateIntradayMinuteCount","Tracker_Steps",
             "Tracker_MinutesVeryActive","Tracker_MinutesFairlyActive",
             "Tracker_MinutesLightlyActive","Tracker_MinutesSedentary",
             "RestingHeartRate","BreathingRate",
             "Hrv_DailyRmssd","SpO2_Avg","ParticipantIdentifier"))

alldata = alldata[,measures]
alldata[,-1] = lapply(alldata[,-1], as.numeric)

data_twodevices = alldata[alldata$ParticipantIdentifier%in%ID_twodevices,]
print("Number of participants who have non-zero HR logs and wear only Sense 2/Charge 5:")
print(length(unique(data_twodevices$ParticipantIdentifier)))
#check_missing_rate(data_twodevices[,-1])
plot_missing_rate(data_twodevices[,-1])
```


#### Based on Participants with Sleep Logs and Sense 2/Charge 5

Only considering default `NA`s from Fitbit:

```{r}
data_sleep_twodevices =  alldata[alldata$ParticipantIdentifier%in%intersect(ID_sleep, ID_twodevices),]
print("Number of participants who have non-zero HR logs and sleep logs and wear only Sense 2/Charge 5:")
print(length(unique(data_sleep_twodevices$ParticipantIdentifier)))
#check_missing_rate(data_sleep_twodevices[,-1])
plot_missing_rate(data_sleep_twodevices[,-1])
```


Updated plot when missingness includes default `NA`s, 0 tracker step counts only:

```{r}
data2 = data_sleep_twodevices
data2[!is.na(data2$Tracker_Steps)&data2$Tracker_Steps==0,-1] = NA  
#check_missing_rate(data2[,-1])
plot_missing_rate(data2[,-1])
```

Updated plot when missingness includes default `NA`s, 0 HeartRateIntradayMinuteCount only:

```{r}
data3 = data_sleep_twodevices
data3[!is.na(data3$HeartRateIntradayMinuteCount)&data3$HeartRateIntradayMinuteCount==0,-1] = NA   
#check_missing_rate(data3[,-1])
plot_missing_rate(data3[,-1])
```

Updated plot when missingness includes default `NA`s, 0 tracker step counts, or 0 HeartRateIntradayMinuteCount:

```{r}
data4 = data_sleep_twodevices
data4[(!is.na(data4$Tracker_Steps)&data4$Tracker_Steps==0)|(!is.na(data4$HeartRateIntradayMinuteCount)&data4$HeartRateIntradayMinuteCount==0),-1] = NA    
#check_missing_rate(data4[,-1])
plot_missing_rate(data4[,-1])
```

Updated plot when missingness includes default `NA`s, 0 tracker step counts, or HeartRateIntradayMinuteCount < 600 minutes:

```{r}
data5 = data_sleep_twodevices
data5[(!is.na(data5$Tracker_Steps)&data5$Tracker_Steps==0)|(!is.na(data4$HeartRateIntradayMinuteCount)&data4$HeartRateIntradayMinuteCount<600),-1] = NA   
#check_missing_rate(data5[,-1])
plot_missing_rate(data5[,-1])
```

Distributions of `HeartRateIntradayMinuteCount` conditional on sleep stages and the presence of `RestingHeartRate`/`Hrv_DailyRmssd`/`SpO2_Avg` logs : 

```{r}
plothr = function(df, variable){
  print(describe(df$HeartRateIntradayMinuteCount[!is.na(df[,variable])]))
  hist(df$HeartRateIntradayMinuteCount[!is.na(df[,variable])], 
       xlab="HeartRateIntradayMinuteCount", main=paste("When", variable, "are present"))
  print(describe(df$HeartRateIntradayMinuteCount[is.na(df[,variable])]))
  hist(df$HeartRateIntradayMinuteCount[is.na(df[,variable])], 
       xlab="HeartRateIntradayMinuteCount", main=paste("When", variable, "are missing"))
}
plothr(data_sleep_twodevices, "Duration_Sleeplogs_Stages")
plothr(data_sleep_twodevices, "RestingHeartRate")
plothr(data_sleep_twodevices, "Hrv_DailyRmssd")
plothr(data_sleep_twodevices, "SpO2_Avg")

```



### Missingness Rates Across Participants

The idea is to check the proportion of days a participant has invalid data for key Fitbit metrics (e.g., heart rate, step, SpO2, HRV). Here, invalid data are defined by zero values and `NA`s as returned by Fitbit devices.

For those with unusually high proportion of invalid data (e.g., > 50%), we provide a list of participant IDs and number of devices they wore during the study.

Open questions: 
- Is 50% a reasonable threshold? 

```{r}
check_invalid_IDs = function(data, variable){
  data = data[, c("ParticipantIdentifier",variable)]
  colnames(data)[2] = "VariableofInterest"
  missdays = data %>%
    group_by(ParticipantIdentifier)%>%
    summarise_at(vars(VariableofInterest), ~sum(. != 0, na.rm=T))
  colnames(missdays)[2] = "nonmiss_days"
  totaldays = data %>%
    group_by(ParticipantIdentifier)%>%
    summarise(total_days = n())
  alldata = merge(missdays, totaldays, by="ParticipantIdentifier")
  alldata = alldata %>%
    mutate(miss_days = total_days - nonmiss_days)%>%
    mutate(Prop = round(miss_days/total_days,2))
  hist(alldata$Prop, xlab="Proportions of Missingness Across Participants",main=variable)

  invalid = alldata[alldata$Prop>0.5,]
  invalidIDs = unique(invalid$ParticipantIdentifier)
  invalid$Num_devices = rep(0, nrow(invalid))
  for(i in 1:length(invalidIDs)){
    deviceinfo = unique(fitbit_devices[fitbit_devices$ParticipantIdentifier==invalidIDs[i],"Device"]$Device)
    invalid$Num_devices[i] = length(deviceinfo)
  }
  #head(invalid[order(-invalid$Prop),])
}


```


#### Based on Participants Wearing Only Sense 2/Charge 5

```{r}
par(mfrow=c(2,2))
check_invalid_IDs(data_twodevices, "HeartRateIntradayMinuteCount")
check_invalid_IDs(data_twodevices, "RestingHeartRate")
check_invalid_IDs(data_twodevices, "Tracker_Steps")
check_invalid_IDs(data_twodevices, "SpO2_Avg")
check_invalid_IDs(data_twodevices, "Duration_Sleeplogs")
check_invalid_IDs(data_twodevices, "Duration_Sleeplogs_Classic")
check_invalid_IDs(data_twodevices, "Duration_Sleeplogs_Stages")
```


#### Based on Participants with Sleep Logs and Sense 2/Charge 5

```{r}
par(mfrow=c(2,2))
check_invalid_IDs(data_sleep_twodevices, "HeartRateIntradayMinuteCount")
check_invalid_IDs(data_sleep_twodevices, "RestingHeartRate")
check_invalid_IDs(data_sleep_twodevices, "Tracker_Steps")
check_invalid_IDs(data_sleep_twodevices, "SpO2_Avg")
check_invalid_IDs(data_sleep_twodevices, "Duration_Sleeplogs")
check_invalid_IDs(data_sleep_twodevices, "Duration_Sleeplogs_Classic")
check_invalid_IDs(data_sleep_twodevices, "Duration_Sleeplogs_Stages")
```



```{r,eval=FALSE}
pid = "RA11101-00364" #RA11101-00184
p_intraday = arrow::open_dataset(s3_external$path(valid_paths[7])) %>% 
    dplyr::filter(ParticipantIdentifier==pid) %>% 
    dplyr::collect()
unique(p_intraday$Type)
p_intraday_hr = p_intraday[p_intraday$Type=="activities-heart",c("ParticipantIdentifier","DateTime","Type","Value")]
p_intraday_steps = p_intraday[p_intraday$Type=="activities-steps",c("ParticipantIdentifier","DateTime","Type","Value")]

pid = "RA11003-00007"
p_sleep = fitbit_sleeplogs[fitbit_sleeplogs$ParticipantIdentifier==pid,]
p_activity = fitbit_activitylogs[fitbit_activitylogs$ParticipantIdentifier==pid,c("ParticipantIdentifier","StartDate","EndDate","Date2","SedentaryMinutes", "LightlyMinutes", "FairlyMinutes", "VeryMinutes", "Steps")]
p_daily = new2_fitbit_daily[new2_fitbit_daily$ParticipantIdentifier==pid,c("ParticipantIdentifier","Date","HeartRateIntradayMinuteCount","Tracker_MinutesFairlyActive","Tracker_MinutesLightlyActive","Tracker_MinutesSedentary","Tracker_MinutesVeryActive","Tracker_Steps","SedentaryMinutes_Activitylogs", "LightlyMinutes_Activitylogs", "FairlyMinutes_Activitylogs", "VeryMinutes_Activitylogs", "Steps_Activitylogs")]

```

  

<!-- ### Differences between `Tracker_Steps` and `Steps` -->

<!-- - `Tracker_Steps`: Steps taken; only includes tracker sources, not manually-entered data. -->
<!-- - `Steps`: Steps taken. -->

<!-- Rows where `Steps` < `Tracker_Steps`: -->

```{r, eval=FALSE}
fitbit_steps = fitbit_daily[,c("ParticipantIdentifier","Date","Steps","Tracker_Steps")]
fitbit_steps$Steps =  as.numeric(fitbit_steps$Steps)
fitbit_steps$Tracker_Steps =  as.numeric(fitbit_steps$Tracker_Steps)
fitbit_steps$diff = fitbit_steps$Steps - fitbit_steps$Tracker_Steps
#nrow(fitbit_steps[fitbit_steps$diff>0&!is.na(fitbit_steps$diff),])
df_to_print = fitbit_steps[fitbit_steps$diff<0&!is.na(fitbit_steps$diff),]
arrange(df_to_print, ParticipantIdentifier, Date)
```
