---
title: "Participants and Devices Insights"
author: "Pranav Anbarasu"
date: "`r base::date()`"
output:
  html_document:
    embed-resources: true
    toc: true
    toc_float:
      smooth-scroll: true
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/RECOVER-MHDR-Analysis/')
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.height = 8)
knitr::opts_chunk$set(fig.width = 15)
```

```{r libraries and archive version, include=FALSE, warning=FALSE, message=FALSE}

library(lubridate)
library(stringr)
library(dplyr)
library(arrow)
library(tidyr)
library(synapser)
library(knit2synapse)
library(ggpubr)

ARCHIVE_VERSION <- "2024-04-23"

if (!(ARCHIVE_VERSION %in% list.dirs("./dashboards/participants-and-devices/rendered-dfs/"))) {
  dir.create(glue::glue("./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/"))
}
```

Using data from external parquet archive version: `r ARCHIVE_VERSION`

```{r access data, include=FALSE, message=FALSE, warning=FALSE}

synLogin(authToken = Sys.getenv("SYNAPSE_AUTH_TOKEN"))

sts_token <- 
  synapser::synGetStsStorageToken(
    entity = 'syn52506069',
    permission = 'read_only',
    output_format = 'json')

s3 <- 
  arrow::S3FileSystem$create(
    access_key = sts_token$accessKeyId,
    secret_key = sts_token$secretAccessKey,
    session_token = sts_token$sessionToken,
    region="us-east-1")

bucket_path <- paste0(sts_token$bucket, '/', 
                      sts_token$baseKey, '/', 
                      ARCHIVE_VERSION, '/')

dataset_list <- 
  s3$GetFileInfo(
    arrow::FileSelector$create(
      bucket_path, 
      recursive=F))

dataset_paths <- character()
for (dataset in dataset_list) {
  dataset_paths <- c(dataset_paths, dataset$path)
}
```


```{r get datasets, include=FALSE}

enrolled <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_enrolledparticipants$", dataset_paths)]))

enrolled_symptoms <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_enrolledparticipants_customfields_symptoms$", dataset_paths)]))

enrolled_treatments <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_enrolledparticipants_customfields_treatments$", dataset_paths)]))

fitbit_actlogs <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitactivitylogs$", dataset_paths)]))

fitbit_dailydata <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitdailydata$", dataset_paths)]))

fitbit_devices <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitdevices$", dataset_paths)]))

fitbit_ecg <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitecg$", dataset_paths)]))

fitbit_ecg_waveformsamples <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitecg_waveformsamples$", dataset_paths)]))

fitbit_intracomb <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitintradaycombined$", dataset_paths)])) %>% 
  select(ParticipantIdentifier) %>% 
  distinct()

fitbit_rhr <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitrestingheartrates$", dataset_paths)]))

fitbit_sleeplogs <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitsleeplogs$", dataset_paths)]))

fitbit_sleeplogdetail <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_fitbitsleeplogs_sleeplogdetails$", dataset_paths)]))

googlefit <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_googlefitsamples$", dataset_paths)]))

hk_activitysummaries <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2activitysummaries$", dataset_paths)]))

hk_ecg <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2electrocardiogram$", dataset_paths)]))

hk_ecg_subsamples <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2electrocardiogram_subsamples$", dataset_paths)]))

hk_heartbeat <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2heartbeat$", dataset_paths)]))

hk_heartbeat_subsamples <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2heartbeat_subsamples$", dataset_paths)]))

hk_samples <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2samples$", dataset_paths)])) %>% 
  select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate)

hk_stats <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2statistics$", dataset_paths)]))

hk_workouts <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2workouts$", dataset_paths)]))

hk_workouts_events <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_healthkitv2workouts_events$", dataset_paths)]))

symptomlog <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_symptomlog$", dataset_paths)]))

symptomlog_symptoms <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_symptomlog_value_symptoms$", dataset_paths)]))

symptomlog_treatments <- 
  arrow::open_dataset(
    s3$path(
      dataset_paths[grep(".*dataset_symptomlog_value_treatments$", dataset_paths)]))
```


```{r all participants by dataset, include=FALSE}

all_participants_by_dataset <- tibble(dataset = character(), ParticipantIdentifier = character())
all_participants_by_dataset <- 
  bind_rows(
    all_participants_by_dataset,
    (enrolled %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'enrolledparticipants') %>% collect()),
    (enrolled_symptoms %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'enrolledparticipants') %>% collect()),
    (enrolled_treatments %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'enrolledparticipants') %>% collect()),
    (fitbit_actlogs %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'fitbit') %>% collect()),
    (fitbit_dailydata %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'fitbit') %>% collect()),
    (fitbit_devices %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'fitbit') %>% collect()),
    (fitbit_ecg %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'fitbit') %>% collect()),
    (fitbit_intracomb %>%
       select(ParticipantIdentifier) %>% 
       distinct() %>% 
       mutate(dataset = 'fitbit') %>% collect()),
    (fitbit_rhr %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'fitbit') %>% collect()),
    (fitbit_sleeplogs %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'fitbit') %>% collect()),
    (googlefit %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'googlefit') %>% collect()),
    (hk_activitysummaries %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'healthkit') %>% collect()),
    (hk_ecg %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'healthkit') %>% collect()),
    (hk_heartbeat %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'healthkit') %>% collect()),
    (hk_samples %>%
       select(ParticipantIdentifier) %>% 
       distinct() %>% 
       mutate(dataset = 'healthkit') %>% collect()),
    (hk_stats %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'healthkit') %>% collect()),
    (hk_workouts %>% 
       select(ParticipantIdentifier) %>% 
       mutate(dataset = 'healthkit') %>% collect()),
    (symptomlog %>% 
      select(ParticipantIdentifier) %>% 
      mutate(dataset = 'symptomlog')) %>% collect()) %>% 
  group_by(dataset, ParticipantIdentifier) %>% 
  distinct() %>% 
  ungroup()
```


```{r merge healthkit device datasets, include=FALSE, cache.lazy=FALSE}

# Unique HealthKit Devices ------------------------------------------------
if (ARCHIVE_VERSION >= "2024-02-29") {
  hk_devices <- bind_rows(
    (hk_ecg %>% 
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate) %>% 
       mutate(Source_Identifier = gsub('com\\.apple\\.health.*', 'com.apple.health', Source_Identifier)) %>% 
       collect()),
    (hk_heartbeat %>% 
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion,StartDate) %>% 
       mutate(Source_Identifier = NA) %>% 
       collect()),
    (hk_samples %>%
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate) %>%
       mutate(Source_Identifier = gsub('com\\.apple\\.health.*', 'com.apple.health', Source_Identifier)) %>% 
       collect()),
    (hk_workouts %>% 
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate) %>% 
       mutate(Source_Identifier = gsub('com\\.apple\\.health.*', 'com.apple.health', Source_Identifier)) %>% 
       group_by(Device_Model, Device_HardwareVersion, Source_Identifier) %>% 
       collect())
  )
} else {
  hk_devices <- bind_rows(
    (hk_ecg %>% 
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate) %>% 
       mutate(Source_Identifier = gsub('com\\.apple\\.health.*', 'com.apple.health', Source_Identifier)) %>% 
       collect()),
    (hk_heartbeat %>% 
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate) %>% 
       mutate(Source_Identifier = gsub('com\\.apple\\.health.*', 'com.apple.health', Source_Identifier)) %>% 
       collect()),
    (hk_samples %>%
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate) %>%
       mutate(Source_Identifier = gsub('com\\.apple\\.health.*', 'com.apple.health', Source_Identifier)) %>% 
       collect()),
    (hk_workouts %>% 
       select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier, StartDate) %>% 
       mutate(Source_Identifier = gsub('com\\.apple\\.health.*', 'com.apple.health', Source_Identifier)) %>% 
       group_by(Device_Model, Device_HardwareVersion, Source_Identifier) %>% 
       collect())
  )
}
```


```{r devices per participant, include=FALSE}

# Devices per Participant -------------------------------------------------
devices_per_pid_fitbit <- 
  fitbit_devices %>% 
  select(ParticipantIdentifier, Device, Type) %>% 
  group_by(ParticipantIdentifier) %>%
  summarise(n_devices_per_participant = n_distinct(Device)) %>% 
  group_by(n_devices_per_participant) %>% 
  count() %>% 
  ungroup() %>% 
  rename(n_participants = n) %>% 
  mutate(dataset = 'fitbit') %>% 
  collect()

devices_per_pid_googlefit <- 
  googlefit %>% 
  select(ParticipantIdentifier, OriginalDataSourceDeviceModel, OriginalDataSourceDeviceType) %>% 
  collect() %>% 
  rename(DeviceModel=OriginalDataSourceDeviceModel,
         DeviceType=OriginalDataSourceDeviceType) %>% 
  group_by(ParticipantIdentifier) %>% 
  summarise(n_devices_per_participant = n_distinct(DeviceModel)) %>% 
  group_by(n_devices_per_participant) %>% 
  count() %>% 
  ungroup() %>% 
  rename(n_participants = n) %>% 
  mutate(dataset = 'googlefit')

devices_per_pid_hk <- 
  hk_devices %>% 
  select(ParticipantIdentifier, Device_HardwareVersion) %>% 
  group_by(ParticipantIdentifier) %>% 
  summarise(n_devices_per_participant = n_distinct(Device_HardwareVersion)) %>% 
  group_by(n_devices_per_participant) %>% 
  count() %>% 
  ungroup() %>% 
  rename(n_participants = n) %>% 
  mutate(dataset = 'healthkit') %>% 
  collect()
```


```{r create device data mismatch dataframes, include=FALSE}

# Number of Participants Without Device Data Found in Non-Device Files ----
mismatch_pids <- 
  list(
    fitbit = 
      all_participants_by_dataset %>% 
      filter(dataset=="fitbit") %>% 
      pull(ParticipantIdentifier) %>% 
      unique() %>% 
      sort() %>% 
      setdiff(fitbit_devices %>% 
                select(ParticipantIdentifier, Device) %>% 
                # collect() %>% 
                filter(!(is.na(Device))) %>%
                pull(ParticipantIdentifier) %>% 
                unique() %>% 
                sort()),
    googlefit = 
      all_participants_by_dataset %>% 
      filter(dataset=="googlefit") %>% 
      pull(ParticipantIdentifier) %>% 
      unique() %>% 
      sort() %>% 
      setdiff(googlefit %>% 
                select(ParticipantIdentifier, OriginalDataSourceDeviceModel, OriginalDataSourceDeviceType) %>% 
                # collect() %>% 
                filter(!(is.na(OriginalDataSourceDeviceModel) & is.na(OriginalDataSourceDeviceType))) %>% 
                pull(ParticipantIdentifier) %>% 
                unique() %>% 
                sort()),
    healthkit = 
      all_participants_by_dataset %>% 
      filter(dataset=="healthkit") %>% 
      pull(ParticipantIdentifier) %>% 
      unique() %>% 
      sort() %>% 
      setdiff(hk_devices %>% 
                select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier) %>% 
                # collect() %>% 
                filter(!(is.na(Device_Model) & is.na(Device_HardwareVersion) & is.na(Source_Identifier))) %>% 
                pull(ParticipantIdentifier) %>% 
                unique() %>% 
                sort())
  )

```

## Count of Unique Participants {.tabset}

### By Cohort

```{r count unique participants by cohort, echo=FALSE}
pq_pids_by_cohort <- 
  all_participants_by_dataset %>%
  group_by(cohort = case_when(
    startsWith(ParticipantIdentifier, "RA") ~ "Adult",
    startsWith(ParticipantIdentifier, "RP") ~ "Pediatric",
    TRUE ~ "Other"
  )) %>%
  summarise(n_participants = n_distinct(ParticipantIdentifier)) %>% 
  mutate(pct = round(100*n_participants/sum(n_participants), 2))

p1 <- 
  pq_pids_by_cohort %>% 
  arrange(desc(n_participants)) %>% 
  ggpubr::ggbarplot(x = "cohort",
                    y = "n_participants", 
                    label = TRUE, 
                    color = "grey25", 
                    fill = "cohort") %>% 
  ggpar(legend = "none")

p2 <- 
  pq_pids_by_cohort %>% 
  ggpie(x = "n_participants",
        label = paste0(pq_pids_by_cohort$cohort, " (", pq_pids_by_cohort$pct, "%)"),
        fill = "cohort")

ggarrange(p1, p2, nrow = 1)

write.csv(pq_pids_by_cohort, glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_pids_by_cohort.csv'), row.names = F)
```

### Per Dataset

```{r count unique participants by dataset, echo=FALSE}
pq_pids_by_dataset <- 
  all_participants_by_dataset %>% 
  group_by(dataset) %>% 
  summarise(n_participants = n_distinct(ParticipantIdentifier))
pq_pids_by_dataset <- pq_pids_by_dataset[match(c("fitbit", "healthkit", "googlefit", "symptomlog", "enrolledparticipants"), pq_pids_by_dataset$dataset), ]

pq_pids_by_dataset %>% 
  arrange(desc(n_participants)) %>% 
  ggpubr::ggbarplot(x = "dataset", 
                    y = "n_participants", 
                    label = TRUE,
                    color = "grey25", 
                    fill = "grey25") %>% 
  ggpar(legend = "none")

write.csv(pq_pids_by_dataset, glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_pids_by_dataset.csv'), row.names = F)
```

### Contributing to Multiple Datasets
```{r count participants contributing to multiple datasets, echo=FALSE}
pq_pids_multiple_datasets <- 
  all_participants_by_dataset %>% 
  group_by(ParticipantIdentifier) %>%
  summarise(n_datasets_contributing_to = n_distinct(dataset)) %>%
  group_by(n_datasets_contributing_to) %>%
  summarise(n_participants = n())

pq_pids_multiple_datasets %>% 
  arrange(desc(n_participants)) %>% 
  mutate(n_datasets_contributing_to = as.factor(n_datasets_contributing_to)) %>% 
  ggpubr::ggbarplot(x = "n_datasets_contributing_to", 
                    y = "n_participants",
                    label = TRUE,
                    color = "grey25", 
                    fill = "grey25") %>% 
  ggpar(legend = "none")

write.csv(pq_pids_multiple_datasets,
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_pids_multiple_datasets.csv'), 
          row.names = F)
```


## Count of Records

A record is a single row in a parquet dataset (after removal of duplicate data)

```{r count records dataframe, echo=FALSE}
pq_n_records <- tibble()
for (dir in dataset_paths) {
  rows <- open_dataset(s3$path(dir)) %>% nrow()
  name <- basename(dir)
  current <- tibble(dataset = name, n_records = rows)
  pq_n_records <- bind_rows(pq_n_records, current)
}
```

```{r record count per dataset viz, echo=FALSE}
p1 <- 
  pq_n_records %>% 
  arrange(desc(n_records)) %>% 
  filter(n_records >= quantile(n_records, 0.75)) %>%
  ggpubr::ggbarplot(x = "dataset", 
                    y = "n_records",
                    # label = F,
                    # lab.pos = "in",
                    # lab.hjust = .4,
                    color = "grey25", 
                    fill = "grey25", 
                    title = "Dataset Record Count") %>% 
  ggpar(legend = "none", 
        rotate = T, subtitle = "For n_records > 75th percentile")

p2 <- 
  pq_n_records %>% 
  arrange(desc(n_records)) %>% 
  filter(n_records >= quantile(n_records, 0.75)) %>%
  filter(dataset!="dataset_fitbitintradaycombined") %>% 
  ggpubr::ggbarplot(x = "dataset", 
                    y = "n_records",
                    # label = F,
                    # lab.pos = "in",
                    # lab.hjust = .4,
                    color = "grey25", 
                    fill = "grey25", 
                    title = "Dataset Record Count") %>% 
  ggpar(legend = "none", 
        rotate = T, subtitle = "For n_records > 75th percentile; excluding dataset_fitbitintradaycombined")

ggarrange(p1, p2, ncol = 1)

write.csv((pq_n_records %>% arrange(desc(n_records))),
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_records_per_dataset.csv'),
          row.names = F)
```
<details>
<summary>Expand for full table</summary>

```{r record count per dataset table, echo=FALSE}
pq_n_records %>% 
      arrange(desc(n_records)) %>% 
      knitr::kable(format = "markdown", 
                   format.args = list(big.mark = ",",
                                      scientific = F))
```

</details>

<!-- ### Average number of days of data per participant -->

```{r}

```

## Device Metrics

### Unique Devices {.tabset}

#### Fitbit

```{r unique devices fitbit viz, echo=FALSE}
pq_pids_by_fitbit_devices <- 
  fitbit_devices %>% 
  select(ParticipantIdentifier, Device, Type) %>% 
  group_by(Device, Type) %>% 
  summarise(n_participants = n_distinct(ParticipantIdentifier), .groups = 'keep') %>% 
  arrange(desc(n_participants)) %>% 
  collect() %>% 
  ungroup()

pq_pids_by_fitbit_devices %>% 
  ggpubr::ggbarplot(x = "Device",
                    y = "n_participants",
                    top = 5,
                    fill = "grey25",
                    color = "grey25",
                    # palette = "Paired",
                    # position = position_dodge(0.9)
                    title = "Unique Device Count - Fitbit") %>%
  ggpubr::ggpar(rotate = T, 
                # font.ytickslab = 8,
                subtitle = "For top 5 values of n_participants")

write.csv(pq_pids_by_fitbit_devices,
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_pids_by_fitbit_devices.csv'),
          row.names = F)
```

<details>
<summary>Expand for full table</summary>

```{r unique devices fitbit table, echo=FALSE}
pq_pids_by_fitbit_devices %>% 
      knitr::kable(format = "markdown", format.args = list(big.mark = ","))
```

</details>

#### Google Fit

```{r unique devices google fit viz, echo=FALSE}
pq_pids_by_googlefit <- 
  googlefit %>% 
  select(ParticipantIdentifier, OriginalDataSourceDeviceModel, OriginalDataSourceDeviceType) %>% 
  group_by(OriginalDataSourceDeviceModel, OriginalDataSourceDeviceType) %>% 
  summarise(n_participants = n_distinct(ParticipantIdentifier), .groups = 'keep') %>% 
  arrange(desc(n_participants)) %>% 
  rename(DeviceModel=OriginalDataSourceDeviceModel,
         DeviceType=OriginalDataSourceDeviceType) %>% 
  collect()

pq_pids_by_googlefit %>% 
  ggpubr::ggbarplot(x = "DeviceModel",
                    y = "n_participants",
                    top = 5,
                    fill = "grey25",
                    color = "grey25",
                    # palette = "Paired",
                    # position = position_dodge(0.9)
                    title = "Unique Device Count - Google Fit") %>%
  ggpubr::ggpar(rotate = T, 
                # font.ytickslab = 8,
                subtitle = "For top 5 values of n_participants")

write.csv(pq_pids_by_googlefit, 
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_pids_by_googlefit.csv'),
          row.names = F)
```

<details>
<summary>Expand for full table</summary>

```{r unique devices google fit table, echo=FALSE}
pq_pids_by_googlefit %>% 
      knitr::kable(format = "markdown")
```

</details>

#### HealthKit

```{r unique devices large healthkit table, include=FALSE, echo=FALSE}
pq_large_pids_by_hk <- 
  hk_devices %>% 
  group_by(Device_Model, Device_HardwareVersion, Source_Identifier) %>% 
  summarise(n_participants = n_distinct(ParticipantIdentifier), .groups = 'keep') %>% 
  arrange(desc(n_participants)) %>% 
  ungroup()
# pq_large_pids_by_hk %>% rmarkdown::paged_table()
write.csv(pq_large_pids_by_hk, 
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_large_pids_by_hk.csv'), 
          row.names = F)
```

```{r unique devices filtered healthkit viz, echo=FALSE}
pq_filtered_pids_by_hk <- 
  hk_devices %>%
  select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier) %>%
  mutate(Source_Identifier = str_to_lower(Source_Identifier)) %>%
  mutate(Source = ifelse(
    !is.na(Device_HardwareVersion) &
      grepl("Watch|iPhone", Device_HardwareVersion, ignore.case = TRUE),
    Device_HardwareVersion,
    ifelse(
      !is.na(Device_Model) &
        grepl("withings|garmin|oura|polar", Device_Model, ignore.case = TRUE),
      Device_Model,
      Source_Identifier
    )
  )) %>%
  group_by(Source) %>%
  summarise(n_participants = n_distinct(ParticipantIdentifier), .groups = 'keep') %>%
  arrange(desc(n_participants)) %>% 
  ungroup()

pq_filtered_pids_by_hk %>% 
  ggpubr::ggbarplot(x = "Source",
                    y = "n_participants",
                    top = 5,
                    fill = "grey25",
                    color = "grey25",
                    # palette = "Paired",
                    # position = position_dodge(0.9)
                    title = "Unique Device Count - HealthKit") %>%
  ggpubr::ggpar(rotate = T, 
                # font.ytickslab = 8,
                subtitle = "For top 5 values of n_participants")

write.csv(pq_filtered_pids_by_hk,
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_filtered_pids_by_hk.csv'), 
          row.names = F)
```

<details>
<summary>Expand for full table</summary>

```{r unique devices filtered healthkit table, echo=FALSE}
pq_filtered_pids_by_hk %>% 
      knitr::kable(format = "markdown")
```

</details>

### Devices per Participant

```{r count devices per participant viz, echo=FALSE}
pq_n_devices_per_participant <- 
  bind_rows(devices_per_pid_fitbit, 
          devices_per_pid_googlefit, 
          devices_per_pid_hk) %>% 
  mutate(n_devices_per_participant = as.factor(n_devices_per_participant)) %>% 
  group_by(dataset) %>% 
  arrange(n_devices_per_participant, .by_group = T) %>% 
  select(dataset, everything())

pq_n_devices_per_participant %>% 
  ggpubr::ggbarplot(x = "dataset",
                    y = "n_participants",
                    # top = 5,
                    fill = "n_devices_per_participant",
                    color = "n_devices_per_participant",
                    palette = "Paired",
                    position = position_dodge(0.9),
                    title = "Number of Unique Devices Used by Participants")

write.csv(pq_n_devices_per_participant,
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_n_devices_per_participant.csv'), 
          row.names = F)
```

<details>
<summary>Expand for full table</summary>

```{r count devices per participant table, echo=FALSE}
pq_n_devices_per_participant %>% 
      knitr::kable(format = "markdown")
```

</details>

### Number of Participants Without Device Data Found in Non-Device Files {.tabset}

E.g. N participant IDs were found in the 'fitbit_activitylogs' dataset but not in the 'fitbit_devices' dataset, meaning that device data was missing for those N participants' data in the 'fitbit_activitylogs' dataset. I.e., data for N participants in dataset X are missing associated device data.

#### Fitbit

```{r device data mismatch fitbit viz, echo=FALSE}

pq_device_pids_mismatch <- list()

pq_device_pids_mismatch$fitbit <- 
  data.frame(
    dataset = c("activitylogs", "dailydata", "intradaycombined", "restingheartrate", "sleeplogs", "ecg"),
    n_participants = c(
      mismatch_pids$fitbit %>% intersect(fitbit_actlogs %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$fitbit %>% intersect(fitbit_dailydata %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$fitbit %>% intersect(fitbit_intracomb %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$fitbit %>% intersect(fitbit_rhr %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$fitbit %>% intersect(fitbit_sleeplogs %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$fitbit %>% intersect(fitbit_ecg %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length()
    )
  ) %>% 
  arrange(desc(n_participants))

pq_device_pids_mismatch$fitbit %>% 
  ggpubr::ggbarplot(x = "dataset",
                    y = "n_participants",
                    label = T,
                    fill = "grey25",
                    color = "grey25")

write.csv(pq_device_pids_mismatch$fitbit,
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_device_pids_mismatch_fitbit.csv'), 
          row.names = F)
```


#### Google Fit

```{r device data mismatch googlefit viz, echo=FALSE}
pq_device_pids_mismatch$googlefit <- 
  data.frame(
    dataset = c("googlefit"),
    n_participants = c(
      mismatch_pids$googlefit %>% intersect(googlefit %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length()
    )
  ) %>% 
  arrange(desc(n_participants))

pq_device_pids_mismatch$googlefit %>% 
  ggpubr::ggbarplot(x = "dataset",
                    y = "n_participants",
                    label = T,
                    fill = "grey25",
                    color = "grey25")

write.csv(pq_device_pids_mismatch$googlefit,
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_device_pids_mismatch_googlefit.csv'),
          row.names = F)
```


#### HealthKit

```{r device data mismatch healthkit viz, echo=FALSE}

pq_device_pids_mismatch$healthkit <- 
  data.frame(
    dataset = c("activitysummaries", "ecg", "heartbeat", "samples", "stats", "workouts"),
    n_participants = c(
      mismatch_pids$healthkit %>% intersect(hk_activitysummaries %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$healthkit %>% intersect(hk_ecg %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$healthkit %>% intersect(hk_heartbeat %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$healthkit %>% intersect(hk_samples %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$healthkit %>% intersect(hk_stats %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length(),
      mismatch_pids$healthkit %>% intersect(hk_workouts %>% pull(ParticipantIdentifier) %>% unique() %>% sort()) %>% length()
    )
  ) %>% 
  arrange(desc(n_participants))

pq_device_pids_mismatch$healthkit %>% 
  ggpubr::ggbarplot(x = "dataset",
                    y = "n_participants",
                    label = T,
                    fill = "grey25",
                    color = "grey25")

write.csv(pq_device_pids_mismatch$healthkit,
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/parquet_device_pids_mismatch_healthkit.csv'),
          row.names = F)
```


## Current State of Data

```{r current state of data table fitbit calc, echo=FALSE}
tmp_pids_fitbit_devices <- 
  fitbit_devices %>%
  select(ParticipantIdentifier, Device, Type) %>%
  collect() %>%
  group_by(ParticipantIdentifier, Device, Type) %>%
  arrange(Device) %>% 
  distinct() %>% 
  ungroup() %>% 
  group_by(ParticipantIdentifier) %>% 
  mutate(n_devices = n_distinct(Device)) %>% 
  arrange(ParticipantIdentifier) %>% 
  mutate(mb = ifelse(Device=="MobileTrack", 1, 0)) %>% 
  ungroup()

mobile_track_pids <- 
  tmp_pids_fitbit_devices %>% 
  filter(n_devices==1, mb==1) %>% 
  pull(ParticipantIdentifier) %>% 
  unique()

non_mobile_track_pids <- 
  tmp_pids_fitbit_devices %>% 
  filter(mb==0) %>% 
  filter(!(ParticipantIdentifier %in% mobile_track_pids))
```


```{r current state of data table healthkit, echo=FALSE}
tmp_filtered_pids_hk <-
  hk_devices %>%
  select(ParticipantIdentifier, Device_Model, Device_HardwareVersion, Source_Identifier) %>%
  mutate(Source_Identifier = str_to_lower(Source_Identifier)) %>%
  mutate(Source = ifelse(
    !is.na(Device_HardwareVersion) &
      grepl("Watch|iPhone", Device_HardwareVersion, ignore.case = TRUE),
    Device_HardwareVersion,
    ifelse(
      !is.na(Device_Model) &
        grepl("withings|garmin|oura|polar", Device_Model, ignore.case = TRUE),
      Device_Model,
      Source_Identifier
    )
  )) %>%
  select(ParticipantIdentifier, Source) %>% 
  group_by(ParticipantIdentifier, Source) %>% 
  arrange(Source) %>% 
  distinct() %>% 
  ungroup() %>% 
  group_by(ParticipantIdentifier) %>% 
  mutate(n_devices = n_distinct(Source)) %>% 
  ungroup() %>% 
  arrange(ParticipantIdentifier) %>% 
  filter(str_detect(Source, ".*Watch.*|.*watch.*", negate = FALSE)) %>% 
  filter(str_detect(Source, ".*watche.*|.*owatch.*", negate = TRUE))
```


```{r current state of data table googlefit, echo=FALSE}
tmp_pids_googlefit <- 
  googlefit %>% 
  select(ParticipantIdentifier, OriginalDataSourceDeviceModel, OriginalDataSourceDeviceType) %>% 
  rename(DeviceModel=OriginalDataSourceDeviceModel,
         DeviceType=OriginalDataSourceDeviceType) %>% 
  filter(!(is.na(DeviceModel) & is.na(DeviceType))) %>% 
  group_by(ParticipantIdentifier, DeviceModel) %>% 
  arrange(DeviceModel) %>% 
  distinct() %>% 
  ungroup() %>% 
  group_by(ParticipantIdentifier) %>% 
  collect() %>% 
  mutate(n_devices = n_distinct(DeviceModel)) %>% 
  ungroup() %>% 
  arrange(ParticipantIdentifier) %>% 
  filter(DeviceType=="WATCH")
```


```{r current state of data table combine and output, echo=FALSE}
row_vals <- c("Participants", "Watch/Tracker", "Total Records")
col_vals <- c("Fitbit", "HealthKit", "GoogleFit", "Symptoms", "Total")

curr_state <- matrix(data = NA, nrow = length(row_vals), ncol = length(col_vals))
rownames(curr_state) <- row_vals
colnames(curr_state) <- col_vals

curr_state[1,] <- pq_pids_by_dataset$n_participants

curr_state[2, 1] <- non_mobile_track_pids %>% select(ParticipantIdentifier) %>% n_distinct()
curr_state[2, 2] <- tmp_filtered_pids_hk %>% select(ParticipantIdentifier) %>% n_distinct()
curr_state[2, 3] <- tmp_pids_googlefit %>% select(ParticipantIdentifier) %>% n_distinct()
curr_state[2, 4] <- NA
curr_state[2, 5] <- curr_state[2, 1] + curr_state[2, 2] + curr_state[2, 3]

curr_state[3, 1] <- pq_n_records$n_records[which(grepl("dataset_fitbit*", pq_n_records$dataset))] %>% sum()
curr_state[3, 2] <- pq_n_records$n_records[which(grepl("dataset_healthkitv2*", pq_n_records$dataset))] %>% sum()
curr_state[3, 3] <- pq_n_records$n_records[which(grepl("dataset_google*", pq_n_records$dataset))] %>% sum()
curr_state[3, 4] <- pq_n_records$n_records[which(grepl("dataset_symptomlog*", pq_n_records$dataset))] %>% sum()
curr_state[3, 5] <- curr_state[3, 1] + curr_state[3, 2] + curr_state[3, 3] + curr_state[3, 4]

curr_state <- curr_state %>% as.data.frame()

curr_state %>% knitr::kable(format = "markdown", format.args = list(big.mark = ","))

write.csv(curr_state, 
          glue::glue('./dashboards/participants-and-devices/rendered-dfs/{ARCHIVE_VERSION}/current_state_of_data.csv'),
          row.names = T)
```


## Code used 

```{r provenance, echo=FALSE, results='asis'}

this_file_path <- "dashboards/participants-and-devices/participants-and-devices.Rmd"

latest_file_commit <- 
  gh::gh("/repos/:owner/:repo/commits", 
         owner = "pranavanba", 
         repo = "RECOVER-MHDR-Analysis", 
         path = this_file_path)[[1]]$commit$url %>% 
  {gsub("https://api.github.com/repos/", "https://github.com/", .)} %>% {gsub("/git/commits/", "/blob/", .)} %>% glue::glue("/{this_file_path}")

cat("[GitHub Code](", latest_file_commit, ")")
```


```{r knit into synapse, eval=FALSE, include=FALSE}

tictoc::tic("INFO: Participants and Devices Markdown knit2synapse")

synapser::synLogin()

### Please install v1.28 of reticulate, as this is the needed version for synapser
### devtools::install_version("reticulate", version = "1.28", repos = "http://cran.us.r-project.org")
DASHBOARD_FOLDER_SYNID <- "syn58643693"
FOLDER_NAME <- "Participants and Devices"

# knit2synapse:::createAndKnitToFolderEntityClient(
#   file = "dashboards/participants-and-devices/participants-and-devices.Rmd",
#   parentId = DASHBOARD_FOLDER_SYNID,
#   folderName = FOLDER_NAME)

knit2synapse::knitfile2synapse(
  file = "dashboards/participants-and-devices/participants-and-devices.Rmd",
  owner = "syn51105296",
  parentWikiId = '627716',
  wikiName = FOLDER_NAME,
  overwrite = TRUE)

tictoc::toc()
```
